### 2014-05-28 ACL2014/experiments.tex
Added new experiments and bib file

\section{Experiments}
We evaluate our  distributed large-scale approximate similarity framework by conducting 
several experiments on a publicly available query logs and 
large-scale query logs sampled from a commercial search engine.

\subsection{Data}
The public dataset that we demonstrate result on is adapted from the query logs of AOL (\aol dataset) search engine \cite{Pass06}. 
Moreover, we show results on large-scale query logs (billion queries) sampled from a commercial search engine. The \dataA  
denotes $1$\% sampled query logs from a commercial search engine, \dataB ($10$\%), and  \dataC ($100$\%). 
Each query point has an associated feature vector, that is high dimensional and sparse. 
Feature vector contains the  webpages (urls) that are weighted based on click through rate on the urls for the query term.  
As a pre-processing step, we remove all those queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our several query-logs datasets. Our biggest dataset has $N=600$ million unique queries 
with billions of unique urls as features.

{\bf Test Data:} We conduct all the experiments on 2000 random queries sampled from the query logs. 
For evaluation, we compute the true similar candidates for all 2000 test queries by calculating cosine similarity 
between 2000 test queries and all the queries in the dataset. In this paper, we set similarity threshold  $\tau=0.7$ 
that means the algorithm need to retrieve candidates that have cosine similarity larger than or equal to $\tau$.

\begin{table}
\centering
\begin{tabular}{|c|r|r|}
\hline
Data & $N$ & $D$  \\ 
\hline
\aol &  $0.3 \times 10^6$  & $0.7 \times 10^6$ \\
\dataA & $6 \times 10^6$  & $66 \times 10^6$ \\
\dataB & $62 \times 10^6$  & $464 \times 10^6$ \\
\dataC &  $617 \times 10^6$  & $ 2.4 \times 10^9$  \\
\hline 
 \end{tabular}
\caption{\footnotesize{Query-logs statistics}}
\label{tab:data}
\end{table}

\subsection{Evaluation Metrics}
We use two metrics for evaluation: Recall and Comparisons. 
Recall is the fraction of \emph{true} similar candidates (found in exact cosine similarity returned candidates) 
retrieved by approximate LSH algorithms.  
Comparisons is the average number of pairwise comparisons per query. 
The goal of this paper is to maximize recall and minimize comparisons.

\subsection{Evaluating Vanilla LSH} 
\label{subsec:eval:vanillaLSH}
In the first experiment, we vary $L=\{1,10,28,55\}$ with fixed $K=16$. 
$L$ denotes the number of tables and $K$ denotes the length of the index of the table. 
If we increase $K$ (increasing the precision to reduce false positives), we also need to 
increase $L$ to get good recall (increasing the recall to reduce false negatives). 
Table \ref{tab:varyL} shows that increasing $L$ leads to better recall, 
however at the expense of more comparisons. In addition, having large $L$ 
means generating large number of random projection bits that is 
both time and memory intensive. Hence, we fix $L=10$, 
which leads to reasonable recall with fewer comparisons.

In the second experiment, we vary $K=\{4,8,16\}$ with fixed $L=10$. 
As expected, Table \ref{tab:varyK} shows that increasing $K$ reduces the number of 
comparisons and worse recall. This is intuitive as we reduce the value of $K$, it leads to 
brute force linear search. Hence, we fix $K=16$ to have fewer number of comparisons.

In the third experiment, we fix $L=10$ and $K=16$ and increase the size of training data. 
Table \ref{tab:varyData} demonstrates that as we increase the training data size, 
the number of comparisons also increase. This result indicates that $K$ and $L$  
needs to be tuned with respect to a specific dataset. $K$ and $L$ can be tuned by 
randomly sampling small set of queries.\footnote{In this paper, we randomly select 2000 queries to tune $K$ and $L$ parameters.}

In the fourth experiment, Table \ref{tab:bestLSH} shows the best $K$ and $L$ parameter settings on different 
sized datasets.\footnote{Recall on \dataC cannot be computed, as it was computationally intensive to find exact similar neighbors.} 
On our biggest dataset of 600 million queries, we set $K=24$, $L=10$. These parameter settings require only 
$464$ comparisons to find approximate nearest neighbors compared to exact cosine similarity that involves 
brute force search over all 600 million queries in the dataset.

\begin{table}
\centering
\begin{tabular}{|c|r|c|}
\hline
$L$ & Comparisons & Recall \\
\hline
1 & 7  & .28 \\
 \rowcolor[gray]{0.9} 10  &  57 & .63 \\
28 &  152 & .77 \\
55 &  297 & .89 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $L$ with fixed $K=16$ on \aol with $\tau=0.7$.}}
\label{tab:varyL}
\end{table}

\begin{table}
\centering
\begin{tabular}{|c|r|c|}
\hline
$K$ & Comparisons & Recall \\
\hline
4  &  112,347 & .98 \\
8 &  11,008 & .90 \\
\rowcolor[gray]{0.9}16 &  57 & .63 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $K$ with fixed $L=10$ on \aol with $\tau=0.7$.}}
\label{tab:varyK}
\end{table}

\begin{table}
\centering
\begin{tabular}{|c|r|c|}
\hline
Data & Comparisons & Recall \\
\hline
\aol & 57  & .63 \\
\dataA  &  1,052 & .67 \\
\dataB    & 10,515 & .64 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Fixed $K=16$  and $L=10$ on different sized datasets with $\tau=0.7$.}}
\label{tab:varyData}
\end{table}

\begin{table}
\centering
\begin{tabular}{|c|r|c|}
\hline
Data & Comparisons & Recall \\
\hline
\aol  ($K=16$) & 57  & .63 \\
\dataA ($K=16$)  &  1,052 & .67 \\
\dataB ($K=20$)   & 695 & .53 \\
\dataC ($K=24$)   & 464 & - \\
\hline 
 \end{tabular}
\caption{\footnotesize{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ on different sized datasets.}}
\label{tab:bestLSH}
\end{table}

\subsection{Evaluating Multi-Probe LSH}
\label{subsec:eval:multiProbeLSH}
In the first experiment, we compare flipping the bits in query only. We evaluate two approaches: \rflipq and \dflipq. We can make several observations from Table \ref{tab:query:aol}: 1) As expected, increasing the number of flips improve recall at expense of more comparisons for both \dflipq and \rflipq. 2) Our results show that \dflipq has significantly better recall than \rflipq with similar number of comparisons. In second row of the table with $F=2$, \dflipq has nine points better recall than \rflipq.

In the second experiment, we compare flipping the bits in both query and the dataset. We can make similar observations from Table \ref{tab:both:aol} as made in the first experiment. In the second row of the Table with $F=2$, \dflipb has thirteen points better recall than \rflipb with similar number of comparisons. Comparing across second row of  Table \ref{tab:query:aol} and \ref{tab:both:aol} shows that flipping the bits in both query and the dataset has better recall at the expense of more comparisons. This is expected as flipping both means that we can find queries at distance two (one flip in query, one flip in dataset), hence more queries in each table when we do probe. Note, we also compared distance based flipping with random flipping on different sized data-sets, and found distance based flipping is always significantly better in terms of recall as compared to random flipping.

In the third experiment, we show the results of both variants of distance based Multi Probe that is \dflipq and \dflipb on different sized datasets. Table \ref{tab:dataset:final} shows the results with parameter $L=10$, $F=2$, and data-size dependent $K$ (same settings of $K$ for different sized datasets is used as in the last experiment of Section \ref{subsec:eval:vanillaLSH}). As observed in the last experiment, flipping bits in both query and the dataset is significantly better in terms of recall (eight points on \dataA and \dataB) with more number of comparisons.

In the fourth experiment, Table \ref{tab:lists} shows the qualitative results for some arbitrary queries. These results are found by applying our system (\dflipb with parameters $L=10$, $K=24$, and $F=2$ ) on \dataC. The first two columns in Table \ref{tab:lists} show that the returned approximate similar neighbors can be useful in finding related queries \cite{Jones06WWW,Jain11SIGIR}. The third column shows an example, where we can find several popular spell errors. The last column shows different variants of a query, where user intends to find out the ``weather in trumbull ct''. Modern search engines provide a direct display with respect to ``weather'' related queries. Hence, if we don't have enough evidence about a specific query being related to ``weather'', we can use queries approximately similar to it to infer that if this query is about ``weather'' or not.

paraphrasing \cite{ganitkevitch13Paraphrase}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c}{\rflipq} & \multicolumn{2}{c}{\dflipq}   \\
\hline
$F$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
1 & 108 & .65 & 106 & .72 \\
2 & 159 & .66 &  {\it155} & {\bf .75}  \\
5 &  311 & .70 &  {\it 303} & {\bf .79}  \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Flipping the bits in the query only with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
\label{tab:query:aol}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c}{\rflipb} & \multicolumn{2}{c}{\dflipb}   \\
\hline
$F$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
1 & 204 & .71 & 192 & .80 \\
 2 & 433 & .73    &  {\it 405} & {\bf .86}  \\
5 &  1557 & .86  & 1475 & .93     \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Flipping the bits in both the query and the dataset with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
\label{tab:both:aol}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c}{\dflipq} & \multicolumn{2}{c}{\dflipb}   \\
\hline
$Data$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
\aol ($K=16$) & 155 & .75 & 405 & .86 \\
\dataA ($K=16$) & 2980 & .76  & 7904  & .84   \\
\dataB ($K=20$) & 1954  & .64 & 5242  & .72     \\
\dataC ($K=24$) & 1280  & -  & 3427 & -      \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ and $F=2$ on different sized datasets with $\tau=0.7$.}}
\label{tab:dataset:final}
\end{table}

\begin{table*}[t]
\centering
\footnotesize \addtolength{\tabcolsep}{-0.5pt} \addtolength{\tabcolsep}{-0.6pt}
{

\begin{tabular}{|c!{\vrule width 1.3pt}c!{\vrule width 1.3pt}c!{\vrule width 1.3pt}c!{\vrule width 1.3pt}c|}
\hline
\textbf{how lbs in a ton}&\textbf{coldwell banker baileys harbor }&\textbf{michaels} &\textbf{trumbull ct weather} \\ %&\textbf{E} \\
%\textbf{how lbs in a ton}&\textbf{coldwell banker baileys harbor }&\textbf{michaels}&\textbf{D}&\textbf{E} \\
\hline
how much lbs is a ton & coldwell banker sturgeon bay wi & maichaels & trumbull ct weather forecast \\
number of pounds in a ton & coldwell banker door county & machaels & weather in trumbull ct  \\
how many lb are in a ton & door county wi mls listings & mechaels   & weather in trumbull ct 06611 \\
How many pounds are in a ton? & door county realtors sturgeon bay & miachaels & trumbull weather forecast \\
how many pounds in a ton & DOOR CTY REAL & michaeils & trumbull ct 06611 \\
1 short ton equals how many pounds & door county coldwell banker & michaelos & trumbull weather ct \\   
how many lbs in a ton? & door realty & michaeks & trumbull ct weather report \\
how many pounds in a ton? & coldwell banker door county horizons & michaeels & trumbull connecticut weather \\ 
How many pounds are in a ton & door county coldwell banker real estate & michaelas & weather 06611  \\
how many lb in a ton & coldwell banker door county wisconsin & michae;ls  & weather trumbull ct  \\
\hline
\end{tabular}
\caption{\footnotesize{Sample $10$ similar neighbors returned by \dflipb with $L=10$, $K=24$, and $F=2$ on \dataC dataset.}}
\label{tab:lists}
}
\end{table*}

### 2014-05-28 ACL2014/abstract.tex
Added missing abstract file

\begin{abstract}
Millions of users visit commercial search engines and  ``query'' their interests.
To provide users with high quality of services, 
search engines such as Bing, Google, and Yahoo require
intelligent analysis to realize users' implicit intents, in particular taking
advantage of very large scaled query logs.  One of the key
interesting tasks involved in learning users' implicit intents often involves 
computing pairwise similarity between all queries.
Due to the large scaled volume that is based on streaming querying, 
computing pairwise similarity is a computationally time intensive task. 
To challenge the aforementioned problem, we exploit  several
Locality Sensitive Hashing (a.k.a, LSH) methods and their novel variants. 
In particular, we develop the framework of LSHs on a distributed system (e.g. Hadoop) to take
advantage of its computing efficiency.

\end{abstract}

### 2014-05-28 ACL2014/system.tex
Added missing latex files

\section{System}
We are interested in finding out, using a batch process, a \emph{small} set of
neighbor candidates for each query such that: 1) the similarity of any
point to a neighbor candidate returned is large and within a user-specified 
similarity threshold ($\tau$). 2) We return an approximate set of neighbor 
candidates with a $100\%$ precision and a large recall.

To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
Our framework has three main steps: 
i) Generate $256$ bit signature for each query.  
ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
Next, generate query pairs which fall in the same table.
iii) Compute cosine similarity between query points which fall in the same table and return the query pairs  
with similarity $\geq\tau$.

To minimize the number of hash functions computations (time intensive to read all features and 
evaluate hash functions to generate a single bit), we use a trick from Andoni and Indyk \shortcite{Andoni08CACM} 
in which hash functions are reused to generate $L$ tables. $K$ vis assumed to be even and $R \approx	\sqrt L$. 
We generate $f(q)=(h_1(q),h_2(q),\dots,h_{k/2}(q)))$ of length $k/2$. 
Next, we define $g(q)=(f_a,f_b)$, where $1\leq a < b \leq R$. This scheme generates $L= \frac{R (R -1)}{2}$. 
This scheme requires O($K  \sqrt L$) hash functions, instead of O($KL$).

 \begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{ll}
\hline
\hline
 \textbf{Symbol} &  \textbf{Description} \\
\hline 
$N$ & \# of query points \\
$D$ & \# of features i.e. all clicked unique urls \\
\hline
\multirow{3}{*}{$K$} & \# of hash functions concatenated together \\ 
   & $g(q)=(h_1(q),h_2(q),\dots,h_k(q)))$ \\ 
	 & to generate the index of a table \\
\hline
 \multirow{2}{*}{$L$} & \# of tables generated independently \\ 
	  &  with $g_j(q)$ index, $\forall 1 \leq j \leq  L$  \\
\hline
$F$ & \# of bits flipped, $\forall 1 \leq j \leq  L$   \\
$\tau$ & $\tau$ threshold \\
Recall & fraction of similar candidates retrieved \\
Comparisons & Avg \# of pairwise comparisons per query  \\
\hline 
\end{tabular}
\caption{\footnotesize{Major Notations}}
}
\label{tab:notation}
\end{table}

\section{Multi Probe LSH}

One strategy that we have experimented with is the following variant of Multi-probe LSH:  first we compute the initial LSH of a query q, which gives the $L$ bucket ids. We then create alternate bucket ids by taking each of the $L$ bucket ids and then creating alternate candidate buckets by flipping a set of coordinates in the LSH of just the query or both the query and the database of queries. We have experimented with two different methods to choose which coordinate to flip: randomly choosing a specified number of coordinates or choosing the set of coordinates based on the distance of q from the random hyperplane that was used in to create this coordinate.  
\subsection{\rflip LSH}
Random Flips

We experimented with flipping the bits in just the query and both the query and the database of all queries.  
1. Generate less number of hash functions
2. Have to compute similarity over less number of data pairs

Advantages of Flipping bits compared to increasing L:
1. Increasing $L$ means generating more random projection bits that is both time and memory intensive.   
%Note, we are already using the trick mentioned in Original LSH to decrease
%the number of tables. Our implementation requires O(sqrt(L)) tables.
2. Probing in more tables for vanilla LSH, hence we need to read data from the disk (more disk read operations.). While Flipping bits, data is
already in memory, and the given data needs to be flipped.
3. Disadvantage of flipping is we need to store random projection distances to perform flipping (which takes space).

\subsection{\dflip LSH}
Based on random projection distance

### 2014-05-29 ACL2014/intro.tex
Added some notes in system.tex

 \section{Introduction}
Many real-world problems on the Web like spelling correction \cite{}, 
finding related queries \cite{Jones06WWW,Jain11SIGIR,Song12WSDM}, finding near-duplicate queries \cite{}, 
and diversifying search results \cite{Song11SIGIR} 
can benefit from query logs from a commercial search engine. 
We can take advantage of large-scale query logs 
by computing pairwise similarity between all queries. Each query point also has an associated feature vector, that is
very high dimensional and sparse $\--$ these are the set of webpages (urls) that
get clicked for this query term.

However, computing pairwise similarity between 
all queries on a commercial large-scale query logs (consisting of hundreds of millions of  queries) 
is a computationally time intensive task. 
To solve this problem, we exploit research advances in Locality Sensitive Hashing 
\cite{Indyk98STOC,Charikar02STOC,Andoni06FOCS,Andoni08CACM}  
to propose an efficient approximate similarity Hadoop framework.

\begin{itemize}
\item We present a distributed system that can approximately compute pairwise similarity 
between all queries on a commercial large-scale query logs in a time efficient manner. 
Can we claim something more specific wrt time (e.g. 0(N logN))?
\item Vanilla LSH 
\item We propose two novel variants of vanilla LSH motivated by the research on Multi-Probe LSH \cite{LvVLDB07}: Random Flipping and Query-Driven Flipping. 
\item  We show that the applicability of our system on two real-world applications like finding related queries (Increasing  direct display coverage is related to finding related queries) and ??.
\end{itemize}

%We are interested in the following setting: given a large set of 
%points $q_1,q_2,\dots,q_n$, each of them is a search-query.

Spelling {grouping mis-spellings in same group}
Similar entities {LOTR,}
Finding related queries

### 2014-05-29 ACL2014/notes.tex
Added some notes in system.tex

Most of the work done in LSH in NLP community uses LSH for dimensionality reduction.

\section{Contributions}
\begin{itemize}
\item We present a distributed system that can approximately compute pairwise similarity 
between all queries on a commercial large-scale query logs in a time efficient manner. 
Can we claim something more specific wrt time (e.g. 0(N logN))?
\item Vanilla LSH 
\item We propose two novel variants of vanilla LSH motivated by the research on Multi-Probe LSH \cite{LvVLDB07}: Random Flipping and Query-Driven Flipping. 
\item  We show that the applicability of our system on two real-world applications like finding related queries (Increasing  direct display coverage is related to finding related queries) and ??.
\end{itemize}

\section{Observations}
\begin{itemize}
\item How to vary $K$ and $L$? The selection of $K$ and $L$ is data dependent. 
If we increase $K$ (increasing the precision to reduce false positives), we also need to 
increase $L$ to get good recall (increasing the recall to reduce false negatives). 
These parameters can be tuned for a specific dataset/application by randomly sampling small set of queries.\footnote{In this paper, we randomly selected 2000 queries to tune $K$ and $L$ parameters.}
\item

\end{itemize}

Advantages of Flipping bits compared to increasing L:
1. Increasing $L$ means generating more random projection bits that is both time and memory intensive.   
%Note, we are already using the trick mentioned in Original LSH to decrease
%the number of tables. Our implementation requires O(sqrt(L)) tables.
2. Probing in more tables for vanilla LSH, hence we need to read data from the disk (more disk read operations.). While Flipping bits, data is
already in memory, and the given data needs to be flipped.
3. Disadvantage of flipping is we need to store random projection distances to perform flipping (which takes space).

### 2014-05-29 ACL2014/system.tex
Added some notes in system.tex

@@
-\section{System}
+\section{Problem Statement}
 We are interested in finding out, using a batch process, a \emph{small} set of
@@
 candidates with a $100\%$ precision and a large recall.
+
+A naive exact brute force algorithm to solve the above problem: 
+1) Compute similarity between each query and all queries in the dataset. 
+2) Return all the queries as neighbors, which have similarity affinity within a similarity threshold ($\tau$).
+
+This algorithm is exact as it has both $100\%$ precision and recall. 
+However, the algorithm is naive as it is not scalable for hundreds of millions of queries. 
+The reason being conducting pairwise computations between all the queries in the dataset involves 
+quadratic number of comparisons in the query dataset size. 
+For hundreds of millions of queries, it means doing petabytes of comparisons; 
+that is be computationally challenging or infeasible even in a distributed setting (such as Hadoop).
+
+The motivated behind this research is to find nearest neighbors by doing a 
+\emph{small} number of comparisons (sublinear in dataset size), instead of brute force linear search. 
+In addition to \emph{small} number of comparisons, we also want to 
+return a set of neighbor candidates with a $100\%$ precision and a large recall. 
+The method we propose meet all these criterions. We do this by exploiting 
+existing research in \lshf (a.k.a., \lsh) and propose their novel variants. 
+In particular, we develop the framework of  \lsh algorithms on a distributed 
+system (e.g. Hadoop) to take advantage of its computing efficiency.
+
+We can not tolerate false positives. 
+We can afford false negatives as there are many relevant queries; not retrieving all of them can be sufficient for a specific problem.
+
+\section{Approach}
+\label{sec:approach}
+We describe a distributed Hadoop framework based on \lshf (\lsh). 
+First, we present vanilla \lsh algorithm based on the seminal research of Andoni and Indyk  \shortcite{Andoni08CACM}.
+To best of our knowledge, this is the first paper that applies this algorithm to NLP applications.
+
+This algorithm improves the existing research in \lsh and \plebf \cite{Indyk98STOC,Charikar02STOC}. 
+\plebf was applied for noun clustering \cite{ravichandran05} and speech \cite {JansenASRU11,JansenIS12}. 
+Recent prior work on new variants of \plebf  \cite{goyal12Flag} for distributional similarity is a special case of Andoni and Indyk's \lsh algorithm.
+
+Next, we present four new variants of vanilla \lsh algorithm motivated by the research on Multi-Probe LSH \cite{LvVLDB07}. 
+A signiﬁcant drawback of vanilla \lsh is the requirement for a large number of hash tables in order to achieve good recall 
+in finding nearest neighbors. The goal of  \mblshf is to get signiﬁcantly better recall than the vanilla \lsh by using 
+the same number of hash tables. The main idea behind \mblshf is to look up multiple buckets within a table that have a high probability 
+of containing the nearest neighbors of a query. We present a high-level idea behind the \mblshf algorithm; 
+for more details, the reader is referred to \cite{LvVLDB07}.
+
+\subsection{Vanilla \lsh}
+\label{sec:vlsh}
+The \lsh algorithm relies on the existence of an \lsh family. Let $H$ be a family of hash functions mapping 
+ $\mathbb{R}^D$ to some universe S. For any two points $p$, $q$; we chose $h\in H$ uniformly at random; 
+ and analyze the probability that $h(p) = h(q)$.  The family $H$ is called a \lsh family if 
+ it satisfies the following conditions:
+
+\begin{enumerate}
+\item $d(p,q) \leq R$, then $Pr[h(p)=h(q)] \geq P_1$ 
+\item $d(p,q) \geq cR$, then $Pr[h(p)=h(q)] \leq P_2$
+\end{enumerate}
+
+A family is generally interesting when  $P_1>P_2$. However, the difference between $P_1$ and $P_2$ can be very small. 
+Given a family $H$ of hash functions with parameters ($R, cR, P_1,P_2$), 
+\lsh algorithm is devised by amplifying the grap between the two probabilities $P_1$ and $P_2$. 
+The pseudo code for vanilla \lsh is shown in Algorithm \ref{alg:vanilla-LSH}.
+
+\mbox{Hadoop Vanilla \lsh} \\
+\mbox{\small {\underline {MAP:}}} \\
+  \FOR j:=1 \TO L \STEP 1 \\
+	     $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$ \\
+
+To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
+Our framework has three main steps: 
+i) Generate $256$ bit signature for each query.  
+ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
+Next, generate query pairs which fall in the same table.
+iii) Compute cosine similarity between query points which fall in the same table and return the query pairs  
+with similarity $\geq\tau$.
 
@@
 
-\section{Multi Probe LSH}
+\subsection{Multi Probe \lsh}
 
-One strategy that we have experimented with is the following variant of Multi-probe LSH:  first we compute the initial LSH of a query q, which gives the $L$ bucket ids.
-We then create alternate bucket ids by taking each of the $L$ bucket ids and then creating alternate candidate buckets by flipping a set of coordinates in the LSH of just the query or both the query and the database of queries.
+One strategy that we have experimented with is the following variant of Multi-probe \lsh:  first we compute the initial \lsh of a query q, which gives the $L$ bucket ids.
+We then create alternate bucket ids by taking each of the $L$ bucket ids and then creating alternate candidate buckets by flipping a set of coordinates in the \lsh of just the query or both the query and the database of queries.
 We have experimented with two different methods to choose which coordinate to flip: randomly choosing a specified number of coordinates or choosing the set of coordinates based on the distance of q from the random hyperplane that was used in to create this coordinate.
-\subsection{\rflip LSH}
+{\rflip \lsh}
 Random Flips
@@
 1. Increasing $L$ means generating more random projection bits that is both time and memory intensive.   
-%Note, we are already using the trick mentioned in Original LSH to decrease
+%Note, we are already using the trick mentioned in Original \lsh to decrease
 %the number of tables. Our implementation requires O(sqrt(L)) tables.
-2. Probing in more tables for vanilla LSH, hence we need to read data from the disk (more disk read operations.). While Flipping bits, data is
+2. Probing in more tables for vanilla \lsh, hence we need to read data from the disk (more disk read operations.). While Flipping bits, data is
 already in memory, and the given data needs to be flipped.
@@
 
-\subsection{\dflip LSH}
+\dflip \lsh
 Based on random projection distance

### 2014-05-29 ACL2014/system.tex
Vanilla LSH algorithm pseudo code

@@
 \lsh algorithm is devised by amplifying the grap between the two probabilities $P_1$ and $P_2$. 
-The pseudo code for vanilla \lsh is shown in Algorithm \ref{alg:vanilla-LSH}.
+The pseudo code written in distributed framework (Hadoop) for vanilla \lsh is shown below:
 
-\mbox{Hadoop Vanilla \lsh} \\
-\mbox{\small {\underline {MAP:}}} \\
-  \FOR j:=1 \TO L \STEP 1 \\
-	     $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$ \\
+%in Algorithm \ref{alg:vanilla-LSH}.
 
-To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
-Our framework has three main steps: 
-i) Generate $256$ bit signature for each query.  
-ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
-Next, generate query pairs which fall in the same table.
-iii) Compute cosine similarity between query points which fall in the same table and return the query pairs  
-with similarity $\geq\tau$.
+{\bf MAP: Input: $N$ queries with their respective feature vectors} \\
+\begin{itemize}
+\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$, where $h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$ are chosen at random from the \lsh family.
+\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. All queries with similar $g_j$ functions ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
+\end{itemize}
 
-To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
-Our framework has three main steps: 
-i) Generate $256$ bit signature for each query.  
-ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
-Next, generate query pairs which fall in the same table.
-iii) Compute cosine similarity between query points which fall in the same table and return the query pairs  
-with similarity $\geq\tau$.
+{\bf REDUCE: Input: Queries ($q=1,2,\dots,M$); $M$ is the number of test queries.} \\
+\begin{itemize}
+\item For each $j=1,2,\dots,L$
+\begin{itemize}
+\item Retrieve all the queries from the bucket with $g_j(q)$ function as the index of the bucket 
+\item Compute cosine similarity between query q and all the retrieved queries. Return all the queries which have similarity affinity within a similarity threshold ($\tau$). 
+\end{itemize}
+\end{itemize}
+
+%To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
+%Our framework has three main steps: 
+%i) Generate $256$ bit signature for each query.  
+%ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
+%Next, generate query pairs which fall in the same table.
+%iii) Compute cosine similarity between query points which fall in the same table and return the query pairs  
+%with similarity $\geq\tau$.
 

### 2014-05-30 ACL2014/abstract.tex
Updated latex files

@@
 \begin{abstract}
-Millions of users visit commercial search engines and  ``query'' their interests.
-To provide users with high quality of services, 
-search engines such as Bing, Google, and Yahoo require
-intelligent analysis to realize users' implicit intents, in particular taking
-advantage of very large scaled query logs.  One of the key
-interesting tasks involved in learning users' implicit intents often involves 
-computing pairwise similarity between all queries.
-Due to the large scaled volume that is based on streaming querying, 
-computing pairwise similarity is a computationally time intensive task. 
-To challenge the aforementioned problem, we exploit  several
-Locality Sensitive Hashing (a.k.a, LSH) methods and their novel variants. 
-In particular, we develop the framework of LSHs on a distributed system (e.g. Hadoop) to take
-advantage of its computing efficiency.
-
+Many Web, Mobile, and NLP applications 
+rely on finding nearest neighbors 
+for a given query from a commercial large-scale query logs . 
+Due to the large scale volume of queries, 
+computing nearest neighbors from all queries using brute force linear 
+search is a computationally time intensive task. 
+To challenge the aforementioned problem, we exploit existing 
+\lshf (a.k.a, \lsh) methods and propose 
+their novel variants in distributed setting (e.g. Hadoop). 
+Our experimental results show that couple of our 
+new variants of \lsh get signiﬁcantly better recall than vanilla \lsh by 
+using the same number of hash tables. 
 \end{abstract}

### 2014-05-30 ACL2014/intro.tex
Updated latex files

@@
  \section{Introduction}
-Many real-world problems on the Web like spelling correction \cite{}, 
-finding related queries \cite{Jones06WWW,Jain11SIGIR,Song12WSDM}, finding near-duplicate queries \cite{}, 
-and diversifying search results \cite{Song11SIGIR} 
-can benefit from query logs from a commercial search engine. 
-We can take advantage of large-scale query logs 
-by computing pairwise similarity between all queries. Each query point also has an associated feature vector, that is
-very high dimensional and sparse $\--$ these are the set of webpages (urls) that
-get clicked for this query term.
+Millions of users visit commercial search engines and ``query'' 
+their interests. To provide users with high quality of services, 
+search engines such as Bing, Google, and Yahoo require
+intelligent analysis to realize users' implicit intents, in particular taking
+advantage of very large scaled query logs.  One of the key
+interesting tasks involved in learning users' implicit intents often involves 
+computing nearest neighbors (queries) for a user given query from all queries. 
+Computing nearest neighbors is useful for 
+many search-related problems on the Web and the Mobile such as 
+finding related queries \cite{Jones06WWW,Jain11SIGIR,Song12WSDM}, 
+finding near-duplicate queries \cite{}, spelling correction \cite{},  
+, paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 
+and diversifying search results \cite{Song11SIGIR}.
 
-However, computing pairwise similarity between 
-all queries on a commercial large-scale query logs (consisting of hundreds of millions of  queries) 
-is a computationally time intensive task. 
-To solve this problem, we exploit research advances in Locality Sensitive Hashing 
-\cite{Indyk98STOC,Charikar02STOC,Andoni06FOCS,Andoni08CACM}  
-to propose an efficient approximate similarity Hadoop framework.
+In this research,  we will take advantage of large-scale query logs 
+by finding nearest neighbors (queries) for a user given query from all 
+queries from a big query logs. Each query point also has an associated feature vector, that is
+very high dimensional and sparse $\--$ these are the set of webpages (urls) that get clicked for this query term.
 
-\begin{itemize}
-\item We present a distributed system that can approximately compute pairwise similarity 
-between all queries on a commercial large-scale query logs in a time efficient manner. 
-Can we claim something more specific wrt time (e.g. 0(N logN))?
-\item Vanilla LSH 
-\item We propose two novel variants of vanilla LSH motivated by the research on Multi-Probe LSH \cite{LvVLDB07}: Random Flipping and Query-Driven Flipping. 
+However, computing nearest neighbors (queries) for a user given query 
+from a commercial large-scale query logs (consisting of hundreds of millions of  queries) is not scalable. 
+The reason being conducting pairwise computations between a given query and all the queries in the dataset involves 
+linear number of comparisons in the query dataset size. For finding neighbors for hundreds of millions of queries, 
+it means doing petabytes of comparisons; that is computationally challenging or infeasible even in a distributed setting (such as Hadoop). 
+In our experiments, our naive Hadoop implementation could not compute neighbors of 
+2000 randomly sampled queries over the commercial query-logs 
+consisting of hundreds of millions of queries.
+
+The motivated behind this research is to find nearest neighbors by doing a 
+\emph{small} number of comparisons (sublinear in dataset size), instead of brute force linear search. 
+In addition to \emph{small} number of comparisons, we also want to 
+return a set of neighbor candidates with a $100\%$ precision and a large recall. 
+The method we propose meet all these criterions. We do this by exploiting 
+existing research in Locality Sensitive Hashing 
+\cite{Indyk98STOC,Charikar02STOC,Andoni06FOCS,Andoni08CACM} and propose their 
+novel variants. In particular, we develop the framework of  \lsh algorithms on a distributed 
+system (e.g. Hadoop) to take advantage of its computing efficiency.
+
+Our work includes following contributions: 
+\begin{enumerate}
+\item We present a distributed system (Hadoop) that can approximately find nearest neighbors for a given query from a commercial large-scale query logs in sublinear time.
+% Can we claim something more specific wrt time (e.g.
+0(N logN))?
+\item We present vanilla \lsh algorithm based on the seminal research of Andoni and Indyk  \shortcite{Andoni08CACM}.
+To best of our knowledge, this is the first paper that applies this algorithm to NLP applications.
+\item We propose four novel variants of vanilla LSH motivated by the research on Multi-Probe LSH \cite{LvVLDB07}.
+We show that two of our variants get signiﬁcantly better recall than the vanilla \lsh by using the same number of hash tables.
+The main idea behind these variants is to intelligently look up multiple buckets within a table that have a high probability of containing the nearest neighbors of a query.
+%: Random Flipping and Query-Driven Flipping. 
 \item  We show that the applicability of our system on two real-world applications like finding related queries (Increasing  direct display coverage is related to finding related queries) and ??.
-\end{itemize}
+\end{enumerate}
 
@@
 
-Spelling {grouping mis-spellings in same group}
-Similar entities {LOTR,}
-Finding related queries
+%Spelling {grouping mis-spellings in same group}
+%Similar entities {LOTR,}
+%Finding related queries

### 2014-05-30 ACL2014/system.tex
Updated latex files

@@
 For hundreds of millions of queries, it means doing petabytes of comparisons; 
-that is be computationally challenging or infeasible even in a distributed setting (such as Hadoop).
+that is  computationally challenging or infeasible even in a distributed setting (such as Hadoop).
 
@@
 A signiﬁcant drawback of vanilla \lsh is the requirement for a large number of hash tables in order to achieve good recall 
-in finding nearest neighbors. The goal of  \mblshf is to get signiﬁcantly better recall than the vanilla \lsh by using 
+in finding nearest neighbors. 
+The goal of  \mblshf is to get signiﬁcantly better recall than the vanilla \lsh by using 
 the same number of hash tables. The main idea behind \mblshf is to look up multiple buckets within a table that have a high probability 
@@
 
-A family is generally interesting when  $P_1>P_2$. However, the difference between $P_1$ and $P_2$ can be very small. 
+A family is generally interesting when  $P_1>P_2$. 
+However, the difference between $P_1$ and $P_2$ can be very small. 
 Given a family $H$ of hash functions with parameters ($R, cR, P_1,P_2$), 
-\lsh algorithm is devised by amplifying the grap between the two probabilities $P_1$ and $P_2$. 
+\lsh algorithm is devised by amplifying the gap between 
+the two probabilities $P_1$ and $P_2$ by concatenating several functions. 
+In particular, \lsh algorithm concatenates $K$ hash functions: 
+$g(q)=(h_1(q),h_2(q),\dots,h_k(q))$. The larger value of $K$ leads to larger 
+gap between probabilites of collision between close queries and far queries; 
+the probabilities are $P_1^{K}$ and $P_2^{K}$ respectively. 
+The advantage of this amplication is that now the algorithm is more precise meaning 
+the probabilty of similar queries falling in same bucket is big; 
+and dis-similar queries falling in same bucket is small.
+
+In addition to the \lsh algorithm being precise, it needs to have large recall. 
+Instead of generating one set of hash tables with index $g(q)=(h_1(q),h_2(q),\dots,h_k(q))$, 
+\lsh algorithm generates $L$ tables, $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$; $\forall 1 \leq j \leq  L$.
+
+%Recall = $1-(1-P_1^{K})^{L}$
+
 The pseudo code written in distributed framework (Hadoop) for vanilla \lsh is shown below:
@@
 \end{itemize}
+
+In this paper, we are interested in cosine similarity, and use the \lsh family defined by Charikar \shortcite{Charikar02STOC}. 
+For two queries; $p,q \in \mathbb{R}^D$, the cosine similarity is $\left( \frac{p.q}{ \| p \| \| q \| }\right)$. 
+The \lsh functions for cosine similarity is defined using sign($\alpha.p$); where $\alpha \in \mathbb{R}^D$ is a random vector. 
+Negative sign is represented as zero and positive sign as one; hence indexes of buckets in hash tables are $K$-sized bit signatures.  
+To generate $\alpha$, we exploit the prior work on 
+generating random projections \cite{Achlioptas03,LiH06} and 
+use hash functions trick to implictly map features ($\mathbb{R}^D$) to a set of \{-1,+1\}.
+\footnote{Note, we respresent our queries ($p$ and $q$) using only non-zero features.}  
+This hashing trick is important and useful as we do not need to explictly store the 
+huge random projection matrix of size $D \times K \times L$.
 

### 2014-05-30 ACL2014/abstract.tex
Updated latex files

@@
 Our experimental results show that couple of our 
-new variants of \lsh get signiﬁcantly better recall than vanilla \lsh by 
+new variants of \lsh get significantly better recall than vanilla \lsh by 
 using the same number of hash tables. 

### 2014-05-30 ACL2014/system.tex
Updated latex files

@@
 Next, we present four new variants of vanilla \lsh algorithm motivated by the research on Multi-Probe LSH \cite{LvVLDB07}. 
-A signiﬁcant drawback of vanilla \lsh is the requirement for a large number of hash tables in order to achieve good recall 
+A significant drawback of vanilla \lsh is the requirement for a large number of hash tables in order to achieve good recall 
 in finding nearest neighbors. 
-The goal of  \mblshf is to get signiﬁcantly better recall than the vanilla \lsh by using 
+The goal of  \mblshf is to get significantly better recall than the vanilla \lsh by using 
 the same number of hash tables. The main idea behind \mblshf is to look up multiple buckets within a table that have a high probability 
@@
 the probabilities are $P_1^{K}$ and $P_2^{K}$ respectively. 
-The advantage of this amplication is that now the algorithm is more precise meaning 
-the probabilty of similar queries falling in same bucket is big; 
+The advantage of this amplification is that now the algorithm is more precise meaning 
+the probability of similar queries falling in same bucket is big; 
 and dis-similar queries falling in same bucket is small.
@@
 generating random projections \cite{Achlioptas03,LiH06} and 
-use hash functions trick to implictly map features ($\mathbb{R}^D$) to a set of \{-1,+1\}.
-\footnote{Note, we respresent our queries ($p$ and $q$) using only non-zero features.}  
-This hashing trick is important and useful as we do not need to explictly store the 
+use hash functions trick to implicitly map features ($\mathbb{R}^D$) to a set of \{-1,+1\}.
+\footnote{Note, we represent our queries ($p$ and $q$) using only non-zero features.}  
+This hashing trick is important and useful as we do not need to explicitly store the 
 huge random projection matrix of size $D \times K \times L$.

### 2014-05-30 ACL2014/experiments.tex
Updated latex files

@@
 The public dataset that we demonstrate result on is adapted from the query logs of AOL (\aol dataset) search engine \cite{Pass06}. 
-Moreover, we show results on large-scale query logs (billion queries) sampled from a commercial search engine. The \dataA  
+Moreover, we show results on large-scale query logs (hundreds of millions of queries) sampled from a commercial search engine. The \dataA  
 denotes $1$\% sampled query logs from a commercial search engine, \dataB ($10$\%), and  \dataC ($100$\%). 
@@
 In the first experiment, we vary $L=\{1,10,28,55\}$ with fixed $K=16$. 
-$L$ denotes the number of tables and $K$ denotes the length of the index of the table. 
+$L$ denotes the number of hash tables and $K$ denotes the length of the index of the buckets in the table. 
 If we increase $K$ (increasing the precision to reduce false positives), we also need to 
@@
 however at the expense of more comparisons. In addition, having large $L$ 
-means generating large number of random projection bits that is 
+means generating large number of random projection bits and hash tables that is 
 both time and memory intensive. Hence, we fix $L=10$, 
@@
 As expected, Table \ref{tab:varyK} shows that increasing $K$ reduces the number of 
-comparisons and worse recall. This is intuitive as we reduce the value of $K$, it leads to 
-brute force linear search. Hence, we fix $K=16$ to have fewer number of comparisons.
+comparisons and worse recall. This is intuitive as  
+the larger value of $K$ leads to larger 
+gap between probabilites of collision between close queries 
+and far queries (see Section \ref{sec:vlsh}). 
+Hence, we fix $K=16$ to have fewer number of comparisons.
 
@@
 Table \ref{tab:varyData} demonstrates that as we increase the training data size, 
-the number of comparisons also increase. This result indicates that $K$ and $L$  
-needs to be tuned with respect to a specific dataset. $K$ and $L$ can be tuned by 
-randomly sampling small set of queries.\footnote{In this paper, we randomly select 2000 queries to tune $K$ and $L$ parameters.}
+the number of comparisons also increase. This result indicates that $K$   
+needs to be tuned with respect to a specific dataset, 
+as large $K$ will reduce the probability of dis-similar 
+queries falling within the same bucket. 
+$K$ and $L$ can be tuned by 
+randomly sampling small set of queries.\footnote{In this paper, we randomly select 2000 queries to tune parameter $K$.}
 
@@
 \dataB    & 10,515 & .64 \\
+\dataC    & - & - \\
 \hline 
@@
 
-paraphrasing \cite{ganitkevitch13Paraphrase}
+% paraphrasing \cite{ganitkevitch13Paraphrase}
+% maybe include deduplication results
 

### 2014-05-31 ACL2014/abstract.tex
Added updated latex file

--- 2014-05-30 ACL2014/abstract.tex
@@
 for a given query from a commercial large-scale query logs . 
-Due to the large scale volume of queries, 
+Due to the large scale volume of user queries, 
 computing nearest neighbors from all queries using brute force linear 
@@
 their novel variants in distributed setting (e.g. Hadoop). 
-Our experimental results show that couple of our 
-new variants of \lsh get signiﬁcantly better recall than vanilla \lsh by 
+Our experimental results show that two of our 
+new variants of \lsh get significantly better recall than vanilla \lsh by 
 using the same number of hash tables. 

### 2014-05-31 ACL2014/applications.tex
Added updated latex file

\section{Applications}
We show the applicability of our nearest neighbors geneated using the approximate \dbflip algorithm with parameters $L=10$, $K=24$, and $F=2$ on two well-known query understanding tasks.

### 2014-05-31 ACL2014/experiments.tex
Added updated latex file

@@
 \label{subsec:eval:vanillaLSH}
-In the first experiment, we vary $L=\{1,10,28,55\}$ with fixed $K=16$. 
+
+\begin{table}
+\centering
+\begin{tabular}{|c|rc|rc|}
+\hline
+\multirow{2}{*}{$\tau$} & \multicolumn{2}{c}{\aol} & \multicolumn{2}{c}{\dataA} \\
+ & Comparisons & Recall & Comparisons & Recall  \\
+\hline
+0.7 & \multirow{3}{*} {57}  & .63  & \multirow{3}{*} {1052} & .67 \\
+0.8 &   & .84  &  & .81 \\
+0.9 &   & .98  &  & .96 \\
+\hline 
+ \end{tabular}
+\caption{\footnotesize{Varying $\tau$ with fixed $K=16$ and $L=10$ on \aol and \dataA.}}
+\label{tab:varyTau}
+\end{table}
+
+In the first experiment, we vary the similarity threshold parameter $\tau={0.7,0.8,0.9}$ 
+with fixed $K=16$ and $L=10$ on \aol and \dataA datasets. 
+Table \ref{tab:varyTau} shows that as expected finding near-duplicates ($0.9$) 
+is easier than nearest neighbors ($0.7$). For, rest of this paper, 
+we fix $\tau=0.7$ as we are interested in both near-duplicates and nearest-neighbors.
+
+In the second experiment, we vary $L=\{1,10,28,55\}$ with fixed $K=16$ on \aol and \dataA datasets. 
 $L$ denotes the number of hash tables and $K$ denotes the length of the index of the buckets in the table. 
@@
 Table \ref{tab:varyL} shows that increasing $L$ leads to better recall, 
-however at the expense of more comparisons. In addition, having large $L$ 
+however at the expense of more comparisons on both the datasets. 
+In addition, having large $L$ 
 means generating large number of random projection bits and hash tables that is 
@@
 
-In the second experiment, we vary $K=\{4,8,16\}$ with fixed $L=10$. 
+\begin{table}
+\centering
+\begin{tabular}{|c|rc|rc|}
+\hline
+\multirow{2}{*}{L} & \multicolumn{2}{c}{\aol} & \multicolumn{2}{c}{\dataA} \\
+ & Comparisons & Recall & Comparisons & Recall  \\
+\hline
+1 & 7  & .28 & 106 & .36 \\
+ \rowcolor[gray]{0.9} 10  &  57 & .63 & 1052 & .67 \\
+28 &  152 & .77 & 2908 & .78 \\
+55 &  297 & .89 & 5648 & .84 \\
+\hline 
+ \end{tabular}
+\caption{\footnotesize{Varying $L$ with fixed $K=16$ on \aol and \dataA with $\tau=0.7$.}}
+\label{tab:varyL}
+\end{table}
+
+In the third experiment, we vary $K=\{4,8,16\}$ with fixed $L=10$ on \aol and \dataA datasets. 
 As expected, Table \ref{tab:varyK} shows that increasing $K$ reduces the number of 
-comparisons and worse recall. This is intuitive as  
+comparisons and worse recall on both the datasets. This is intuitive as  
 the larger value of $K$ leads to larger 
@@
 
-In the third experiment, we fix $L=10$ and $K=16$ and increase the size of training data. 
+\begin{table}
+\centering
+%\begin{tabular}{|c|r|c|}
+\begin{tabular}{|c|rc|rc|}
+\hline
+%$K$ & Comparisons & Recall \\
+\multirow{2}{*}{K} & \multicolumn{2}{c}{\aol} & \multicolumn{2}{c}{\dataA} \\
+ & Comparisons & Recall & Comparisons & Recall  \\
+\hline
+4  &  112,347 & .98 & 2,29,2670 & .96 \\
+8 &  11,008 & .90 & 221,132 & .88 \\
+\rowcolor[gray]{0.9}16 &  57 & .63 & 1,052 & .67 \\
+\hline 
+ \end{tabular}
+\caption{\footnotesize{Varying $K$ with fixed $L=10$ on \aol with $\tau=0.7$.}}
+\label{tab:varyK}
+\end{table}
+
+In the fourth experiment, we fix $L=10$ and $K=16$ and increase the size of training data. 
 Table \ref{tab:varyData} demonstrates that as we increase the training data size, 
@@
 
-In the fourth experiment, Table \ref{tab:bestLSH} shows the best $K$ and $L$ parameter settings on different 
+In the fifth experiment, Table \ref{tab:bestLSH} shows the best $K$ and $L$ parameter settings on different 
 sized datasets.\footnote{Recall on \dataC cannot be computed, as it was computationally intensive to find exact similar neighbors.} 
@@
 brute force search over all 600 million queries in the dataset.
-
-\begin{table}
-\centering
-\begin{tabular}{|c|r|c|}
-\hline
-$L$ & Comparisons & Recall \\
-\hline
-1 & 7  & .28 \\
- \rowcolor[gray]{0.9} 10  &  57 & .63 \\
-28 &  152 & .77 \\
-55 &  297 & .89 \\
-\hline 
- \end{tabular}
-\caption{\footnotesize{Varying $L$ with fixed $K=16$ on \aol with $\tau=0.7$.}}
-\label{tab:varyL}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{|c|r|c|}
-\hline
-$K$ & Comparisons & Recall \\
-\hline
-4  &  112,347 & .98 \\
-8 &  11,008 & .90 \\
-\rowcolor[gray]{0.9}16 &  57 & .63 \\
-\hline 
- \end{tabular}
-\caption{\footnotesize{Varying $K$ with fixed $L=10$ on \aol with $\tau=0.7$.}}
-\label{tab:varyK}
-\end{table}
 
@@
 \dataB    & 10,515 & .64 \\
-\dataC    & - & - \\
+\dataC    & 105,126 & - \\
 \hline 

### 2014-05-31 ACL2014/intro.tex
Updated latex files
Added updated latex file

@@
 intelligent analysis to realize users' implicit intents, in particular taking
-advantage of very large scaled query logs.  One of the key
+advantage of large scaled query logs.  One of the key
 interesting tasks involved in learning users' implicit intents often involves 
@@
 by finding nearest neighbors (queries) for a user given query from all 
-queries from a big query logs. Each query point also has an associated feature vector, that is
-very high dimensional and sparse $\--$ these are the set of webpages (urls) that get clicked for this query term.
+queries from a big query logs. Each query term also has an associated feature vector, that is
+ high dimensional and sparse $\--$ these are the set of webpages (urls) that get clicked for this query term.
 
@@
 
-The motivated behind this research is to find nearest neighbors by doing a 
+The motivation behind this research is to find nearest neighbors by doing a 
 \emph{small} number of comparisons (sublinear in dataset size), instead of brute force linear search. 
@@
 return a set of neighbor candidates with a $100\%$ precision and a large recall. 
+We can not tolerate false positives. We can afford false negatives as there 
+are many relevant queries; not retrieving all of them can be sufficient for a specific problem.
+
 The method we propose meet all these criterions. We do this by exploiting 
@@
 \item We propose four novel variants of vanilla LSH motivated by the research on Multi-Probe LSH \cite{LvVLDB07}.
-We show that two of our variants get signiﬁcantly better recall than the vanilla \lsh by using the same number of hash tables.
+We show that two of our variants achieve significantly better recall than the vanilla \lsh by using the same number of hash tables.
 The main idea behind these variants is to intelligently look up multiple buckets within a table that have a high probability of containing the nearest neighbors of a query.

### 2014-05-31 ACL2014/system.tex
Updated latex files
Added updated latex file

@@
 neighbor candidates for each query such that: 1) the similarity of any 
-point to a neighbor candidate returned is large and within a user-specified 
+query term to a neighbor candidate returned is large and within a user-specified 
 similarity threshold ($\tau$). 2) We return an approximate set of neighbor 
@@
 
-We can not tolerate false positives. 
-We can afford false negatives as there are many relevant queries; not retrieving all of them can be sufficient for a specific problem.
-
 \section{Approach}
@@
 This algorithm improves the existing research in \lsh and \plebf \cite{Indyk98STOC,Charikar02STOC}. 
-\plebf was applied for noun clustering \cite{ravichandran05} and speech \cite {JansenASRU11,JansenIS12}. 
+\plebf was applied for noun clustering \cite{ravichandran05} and speech tasks \cite {JansenASRU11,JansenIS12}. 
 Recent prior work on new variants of \plebf  \cite{goyal12Flag} for distributional similarity is a special case of Andoni and Indyk's \lsh algorithm.
@@
 The goal of  \mblshf is to get significantly better recall than the vanilla \lsh by using 
-the same number of hash tables. The main idea behind \mblshf is to look up multiple buckets within a table that have a high probability 
-of containing the nearest neighbors of a query. We present a high-level idea behind the \mblshf algorithm; 
-for more details, the reader is referred to \cite{LvVLDB07}.
+the same number of hash tables. 
+%The main idea behind \mblshf is to look up multiple buckets within a table that have a high probability 
+%of containing the nearest neighbors of a query. We present a high-level idea behind the \mblshf algorithm; 
+%for more details, the reader is referred to \cite{LvVLDB07}.
 
@@
 The \lsh algorithm relies on the existence of an \lsh family. Let $H$ be a family of hash functions mapping 
- $\mathbb{R}^D$ to some universe S. For any two points $p$, $q$; we chose $h\in H$ uniformly at random; 
+ $\mathbb{R}^D$ to some universe S. For any two query terms $p$, $q$; we chose $h\in H$ uniformly at random; 
  and analyze the probability that $h(p) = h(q)$.  The family $H$ is called a \lsh family if 
@@
 
+In above conditions, $d$ is a distance function\footnote{In this paper, we use cosine distance.}, 
+a distance threshold $R>0$ and an approximation factor $c>1$.
+
 A family is generally interesting when  $P_1>P_2$. 
@@
 In particular, \lsh algorithm concatenates $K$ hash functions: 
-$g(q)=(h_1(q),h_2(q),\dots,h_k(q))$. The larger value of $K$ leads to larger 
+$g(q)=(h_1(q),h_2(q),\dots,h_K(q))$. 
+The larger value of $K$ leads to larger 
 gap between probabilites of collision between close queries and far queries; 
@@
 In addition to the \lsh algorithm being precise, it needs to have large recall. 
-Instead of generating one set of hash tables with index $g(q)=(h_1(q),h_2(q),\dots,h_k(q))$, 
-\lsh algorithm generates $L$ tables, $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$; $\forall 1 \leq j \leq  L$.
+Instead of generating one set of hash table with index $g(q)=(h_1(q),h_2(q),\dots,h_K(q))$, 
+\lsh algorithm generates $L$ tables, $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q)))$; $\forall 1 \leq j \leq  L$.
 
@@
 
-The pseudo code written in distributed framework (Hadoop) for vanilla \lsh is shown below:
-
-%in Algorithm \ref{alg:vanilla-LSH}.
-
-{\bf MAP: Input: $N$ queries with their respective feature vectors} \\
-\begin{itemize}
-\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$, where $h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$ are chosen at random from the \lsh family.
-\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. All queries with similar $g_j$ functions ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
-\end{itemize}
-
-{\bf REDUCE: Input: Queries ($q=1,2,\dots,M$); $M$ is the number of test queries.} \\
-\begin{itemize}
-\item For each $j=1,2,\dots,L$
-\begin{itemize}
-\item Retrieve all the queries from the bucket with $g_j(q)$ function as the index of the bucket 
-\item Compute cosine similarity between query q and all the retrieved queries. Return all the queries which have similarity affinity within a similarity threshold ($\tau$). 
-\end{itemize}
-\end{itemize}
-
+\subsection{\lsh for Cosine Similarity}
+\label{subsec:vlsh:cosine}
 In this paper, we are interested in cosine similarity, and use the \lsh family defined by Charikar \shortcite{Charikar02STOC}. 
@@
 %Next, generate query pairs which fall in the same table.
-%iii) Compute cosine similarity between query points which fall in the same table and return the query pairs  
+%iii) Compute cosine similarity between query terms which fall in the same table and return the query pairs  
 %with similarity $\geq\tau$.
 
-To minimize the number of hash functions computations (time intensive to read all features and 
-evaluate hash functions to generate a single bit), we use a trick from Andoni and Indyk \shortcite{Andoni08CACM} 
-in which hash functions are reused to generate $L$ tables. $K$ vis assumed to be even and $R \approx	\sqrt L$. 
-We generate $f(q)=(h_1(q),h_2(q),\dots,h_{k/2}(q)))$ of length $k/2$. 
+Vanilla \lsh has two main steps: preprocessing the data and querying the database.  
+The pseudo code written for vanilla \lsh is summarized in .
+
+In preprocessing step, the algorithm takes input as $N$ queries with an associated feature vectors. In our setting, 
+feature vector is very high dimensional and sparse; that is the clicked webpages (urls) for a given query term. 
+During preprocessing, first we generate $L\times K$ hash functions. 
+Next, we hash all queries using these hash functions to build $L$ hash tables 
+with each hash table containing at most $2^K$ buckets. 
+There are at most $2^K$ buckets because index of each bucket: $g_j$ is $K$-widith bit index. 
+Each query term is placed in their respective buckets for all  $L$ hash tables.
+
+In querying step, for input $M$ test queries, we retrieve all the query 
+terms which appear in the buckets associated with $M$ test queries. 
+Next, compute cosine similarity between each of the retrieved terms 
+and the input test queries. Return all those queries as neighbors 
+which are within a similarity threshold ($\tau$).
+
+In this research, we have implemented the above algorithm within the distributed setting (Hadoop).   
+In our experiments, we show that the algorithm scales to hundreds of millions of queries (see Section \ref{subsec:eval:vanillaLSH}).
+
+%in Algorithm \ref{alg:vanilla-LSH}.
+
+\fbox{
+\begin{minipage}{2.5in}
+{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors \\
+\begin{itemize}
+\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q)))$, where $h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q)))$ are chosen at random from the \lsh family.
+\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. All queries with similar $g_j$ functions ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
+\end{itemize}
+
+{\bf Query:} Input is queries ($q=1,2,\dots,M$); $M$ is the number of test queries \\
+\begin{itemize}
+\item For each $j=1,2,\dots,L$
+\begin{itemize}
+\item Retrieve all the queries from the bucket with $g_j(q)$ function as the index of the bucket 
+\item Compute cosine similarity between query q and all the retrieved queries. Return all the queries which have similarity affinity within a similarity threshold ($\tau$). 
+\end{itemize}
+\end{itemize}
+\end{minipage}
+}
+
+\subsection{Reusing Hash Functions}
+\label{subsec:resuseHash}
+In Section \ref{subsec:vlsh:cosine}, we showed that vanilla \lsh requires $L\times K$ hash functions. 
+However generating hash functions is computationally expensive as 
+it takes time to read all features and 
+evaluate hash functions over all those features to generate a single bit. 
+To minimize the number of hash functions computations, 
+we use a trick from Andoni and Indyk \shortcite{Andoni08CACM} 
+in which hash functions are reused to generate $L$ tables. $K$ is assumed to be even and $R \approx	\sqrt L$. 
+We generate $f(q)=(h_1(q),h_2(q),\dots,h_{K/2}(q)))$ of length $k/2$. 
 Next, we define $g(q)=(f_a,f_b)$, where $1\leq a < b \leq R$. This scheme generates $L= \frac{R (R -1)}{2}$. 
 This scheme requires O($K  \sqrt L$) hash functions, instead of O($KL$).    
-
+For rest of this paper, we use the above trick to generate $L$ hash tables with $K$-widith bit bucket-ids. 
 \begin{table}
@@
 \hline 
-$N$ & \# of query points \\
+$N$ & \# of query terms \\
 $D$ & \# of features i.e. all clicked unique urls \\
@@
 \subsection{Multi Probe \lsh}
+\label{sec:mblsh}
+As we discussed in Section \ref{subsec:resuseHash} that generating hash functions can be computationally expensive.  
+That is exactly one of the significant drawbacks of vanilla \lsh as it requires a large number of hash tables (large $L$) 
+in order to achieve good recall in finding nearest neighbors.
+Here, We describe four new variants of vanilla \lsh algorithm motivated by the research on \mblshf \cite{LvVLDB07}. 
+The goal of  \mblshf is to get significantly better recall than the vanilla \lsh by using 
+the same number of hash tables. The main concept behind \mblshf is to look 
+up multiple buckets within a table that have a high probability of containing the nearest neighbors of a query. 
+Note, eventhough vanila \lsh and \mblshf both have same number of hash tables ($L$); 
+\mblshf requires more number of probes as it searches in multiple buckets within a table. 
+The main advantage of searching in multiple buckets over generating more number of tables 
+is that it takes more memory and time to generate more tables in pre-processing.
 
-One strategy that we have experimented with is the following variant of Multi-probe \lsh:  first we compute the initial \lsh of a query q, which gives the $L$ bucket ids.
-We then create alternate bucket ids by taking each of the $L$ bucket ids and then creating alternate candidate buckets by flipping a set of coordinates in the \lsh of just the query or both the query and the database of queries.
-We have experimented with two different methods to choose which coordinate to flip: randomly choosing a specified number of coordinates or choosing the set of coordinates based on the distance of q from the random hyperplane that was used in to create this coordinate.
-{\rflip \lsh}
-Random Flips
+The original \mblshf algorithm is developed for Euclidean distance. 
+If interested in details about \mblshf algorithm for Euclidean distance, the reader is referred to \cite{LvVLDB07}. 
+Here, we propose four variants of \mblshf for cosine similarity:
+\begin{itemize}
+\item {\bf \rflipq:} The first variant is our baseline: first we compute the initial \lsh of a query q, which gives the $L$ bucket ids.  
+Next, we create alternate bucket ids by taking each of the $L$ bucket ids and then creating alternate candidate buckets by flipping a 
+set of coordinates randomly in the \lsh of just the query.  
+\item {\bf \rflipb:} The second variant is another baseline similar to the previous one. Instead of just flipping the bits for only the query, 
+here we flip bits for both the query and all the queries in the database. 
+\item {\bf \dflipq:} The third variant is intelligent version of first variant. Instead of randomly flipping some coordinates, 
+we devisely select a set of coordinates based on the distance of query term from the random hyperplane (hash function) 
+that was used in to create this coordinate. 
+The distance of query term from the random hyperplane is the absolute value which we get before applying the sign function on it (see Section \ref{subsec:vlsh:cosine}). 
+\item {\bf \dflipb:} The fourth version is similar to third one, however 
+here we flip bits for both the query and the queries in the database (intelligent version of second baseline). 
+\end{itemize}
 
-We experimented with flipping the bits in just the query and both the query and the database of all queries.  
-1. Generate less number of hash functions
-2. Have to compute similarity over less number of data pairs
+%we have experimented with is the following variant of Multi-probe \lsh:  first we compute the initial \lsh of a query q, which gives the $L$ bucket ids.
 
-Advantages of Flipping bits compared to increasing L:
-1. Increasing $L$ means generating more random projection bits that is both time and memory intensive.   
+%We have experimented with two different methods to choose which coordinate to flip: randomly choosing a specified number of coordinates or choosing the set of coordinates based on the distance of q from the random hyperplane that was used in to create this coordinate.
+%{\rflip \lsh}
+%Random Flips
+
+%We experimented with flipping the bits in just the query and both the query and the database of all queries.  
+%1. Generate less number of hash functions
+%2. Have to compute similarity over less number of data pairs
+
+%Advantages of Flipping bits compared to increasing L:
+%1. Increasing $L$ means generating more random projection bits that is both time and memory intensive.   
 %Note, we are already using the trick mentioned in Original \lsh to decrease
 %the number of tables. Our implementation requires O(sqrt(L)) tables.
-2. Probing in more tables for vanilla \lsh, hence we need to read data from the disk (more disk read operations.). While Flipping bits, data is
-already in memory, and the given data needs to be flipped.
-3. Disadvantage of flipping is we need to store random projection distances to perform flipping (which takes space).
+%2. Probing in more tables for vanilla \lsh, hence we need to read data from the disk (more disk read operations.). While Flipping bits, data is
+%already in memory, and the given data needs to be flipped.
+%3. Disadvantage of flipping is we need to store random projection distances to perform flipping (which takes space).
 
-\dflip \lsh
-Based on random projection distance
+%\dflip \lsh
+%Based on random projection distance

### 2014-05-31 ACL2014/applications.tex
Added updated latex file

@@
 \section{Applications}
-We show the applicability of our nearest neighbors geneated using the approximate \dbflip algorithm with parameters $L=10$, $K=24$, and $F=2$ on two well-known query understanding tasks.
+We show the applicability of our nearest neighbors geneated using 
+the approximate \dflip algorithm with parameters $L=10$, $K=24$, and $F=2$ on 
+two well-known query understanding tasks: finding related queries and removing de-duplcate queries.

### 2014-06-01 ACL2014/abstract.tex
Added abstract and intro updated by Chi Hoon Lee

--- 2014-05-30 ACL2014/abstract.tex
@@
 \begin{abstract}
-Many Web, Mobile, and NLP applications 
-rely on finding nearest neighbors 
-for a given query from a commercial large-scale query logs . 
-Due to the large scale volume of queries, 
-computing nearest neighbors from all queries using brute force linear 
-search is a computationally time intensive task. 
-To challenge the aforementioned problem, we exploit existing 
+Many applications from various domains such as World Wide Web, Mobile, and NLP
+rely on finding nearest neighbors given a data instance.
+Due to the very large scale
+(e.g., users' queries from commercial search engines),
+computing nearest neighbors is often required to
+understand users' intents. However, it is a non-trivial
+task as the computational complexity grow significantly with the number of queries.
+To challenge the aforementioned problem, we exploit 
 \lshf (a.k.a, \lsh) methods and propose 
-their novel variants in distributed setting (e.g. Hadoop). 
-Our experimental results show that couple of our 
-new variants of \lsh get signiﬁcantly better recall than vanilla \lsh by 
-using the same number of hash tables. 
+novel varaints in a distributed computing environment (e.g. Hadoop). 
+The experimental results demonstrate our 
+proposed variants of \lsh achieve the robust performance with better recall compared with Vanilla \lsh even
+when using the same space determined by the number of hash tables .
+
+%Many Web, Mobile, and NLP applications 
+%rely on finding nearest neighbors 
+%for a given query from a commercial large-scale query logs . 
+%Due to the large scale volume of user queries, 
+%computing nearest neighbors from all queries using brute force linear 
+%search is a computationally time intensive task. 
+%To challenge the aforementioned problem, we exploit existing 
+%\lshf (a.k.a, \lsh) methods and propose 
+%their novel variants in distributed setting (e.g. Hadoop). 
+%Our experimental results show that two of our 
+%new variants of \lsh get significantly better recall than vanilla \lsh by 
+%using the same number of hash tables. 
 \end{abstract}

### 2014-06-01 ACL2014/intro.tex
Added abstract and intro updated by Chi Hoon Lee

@@
 interesting tasks involved in learning users' implicit intents often involves 
-computing nearest neighbors (queries) for a user given query from all queries. 
+computing nearest neighbors (queries) for a user given query. 
 Computing nearest neighbors is useful for 
@@
 
-In this research,  we will take advantage of large-scale query logs 
-by finding nearest neighbors (queries) for a user given query from all 
-queries from a big query logs. Each query term also has an associated feature vector, that is
- high dimensional and sparse $\--$ these are the set of webpages (urls) that get clicked for this query term.
+In this research, we focus on finding nearest neighbors for a given query
+from very large scaled query logs available from a commercial search engine. 
+%In order to understand the implicit users' intent, each query is initially represented in a high dimensional feature space,
+%where each dimension corresponds to a clicked url.
+However, computing nearest neighbors of a query 
+from large-scale query logs is a non-trivial task due to the computational complexity among hundreds of millions of  queries.
+%The reason being conducting pairwise computations between a given query and all the queries in the dataset involves 
+%linear number of comparisons in the query dataset size. For finding neighbors for hundreds of millions of queries, 
+%it means doing petabytes of comparisons; that is computationally challenging or infeasible even in a distributed setting (such as Hadoop). 
+Note that even in a distributed computing environment such as Hadoop, the naive pairwise computation is not feasible from our experiments  using 2000 random queries to attempt to retrieve neighbors from the query logs consisting of hundreds of millions of queries.
+In other words, even though the big \textit{O} notation is denoted as linear, \textit{2000*N} comparisons are not feasible when \textit{N} reaches to hundreds of millions.
 
-However, computing nearest neighbors (queries) for a user given query 
-from a commercial large-scale query logs (consisting of hundreds of millions of  queries) is not scalable. 
-The reason being conducting pairwise computations between a given query and all the queries in the dataset involves 
-linear number of comparisons in the query dataset size. For finding neighbors for hundreds of millions of queries, 
-it means doing petabytes of comparisons; that is computationally challenging or infeasible even in a distributed setting (such as Hadoop). 
-In our experiments, our naive Hadoop implementation could not compute neighbors of 
-2000 randomly sampled queries over the commercial query-logs 
-consisting of hundreds of millions of queries.
+In order to address the computational challenge, this paper exploits to find nearest neighbors by doing a 
+\emph{small} number of comparisons -- that is, sublinear in dataset size -- instead of brute force linear search. 
+In addition to \emph{small} number of comparisons, we aim to 
+retrieve neighboring candidates with a $100\%$ precision and a large recall.
+It is important that false positive rate (ratio of  ``incorrectly'' identifying queries as neighbors) is to be penalized more severely than false negative (ratio of missing ``true'' neighbors).
 
-The motivation behind this research is to find nearest neighbors by doing a 
-\emph{small} number of comparisons (sublinear in dataset size), instead of brute force linear search. 
-In addition to \emph{small} number of comparisons, we also want to 
-return a set of neighbor candidates with a $100\%$ precision and a large recall. 
-We can not tolerate false positives. We can afford false negatives as there 
-are many relevant queries; not retrieving all of them can be sufficient for a specific problem.
-
-The method we propose meet all these criterions. We do this by exploiting 
-existing research in Locality Sensitive Hashing 
-\cite{Indyk98STOC,Charikar02STOC,Andoni06FOCS,Andoni08CACM} and propose their 
-novel variants. In particular, we develop the framework of  \lsh algorithms on a distributed 
-system (e.g. Hadoop) to take advantage of its computing efficiency.
+The methods we propose in this paper meet all these criterions by extending existing research in \lshf 
+\cite{Indyk98STOC,Charikar02STOC,Andoni06FOCS,Andoni08CACM}  to novel variants. 
+In particular, we develop the framework of  the variants on a distributed 
+system, Hadoop by taking advantage of its distributed computing power.
 
@@
 \begin{enumerate}
-\item We present a distributed system (Hadoop) that can approximately find nearest neighbors for a given query from a commercial large-scale query logs in sublinear time.
-% Can we claim something more specific wrt time (e.g.
-0(N logN))?
 \item We present vanilla \lsh algorithm based on the seminal research of Andoni and Indyk  \shortcite{Andoni08CACM}.
@@
 The main idea behind these variants is to intelligently look up multiple buckets within a table that have a high probability of containing the nearest neighbors of a query.
+\item We present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial large-scale query logs in sublinear time.
+% Can we claim something more specific wrt time (e.g.
+0(N logN))?
 %: Random Flipping and Query-Driven Flipping. 
-\item  We show that the applicability of our system on two real-world applications like finding related queries (Increasing  direct display coverage is related to finding related queries) and ??.
+\item  We show that the applicability of our system on two real-world applications such as finding related queries and removing duplicated queries.
+%(Increasing  direct display coverage is related to finding related queries) and ??.
 \end{enumerate}

### 2014-06-01 ACL2014/discussion.tex
updated latex files

\section{Discussion and Conclusion}
\label{sec:discuss}
%In this paper, we demonstrated the effectiveness of our p

### 2014-06-01 ACL2014/system.tex
section 2 edits

@@
 \section{Problem Statement}
-We are interested in finding out, using a batch process, a \emph{small} set of
-neighbor candidates for each query such that: 1) the similarity of any 
-query term to a neighbor candidate returned is large and within a user-specified 
-similarity threshold ($\tau$). 2) We return an approximate set of neighbor 
-candidates with a $100\%$ precision and a large recall.
+We start with a corpus of user queries being represented as vectors
+over some domain (e.g. URLs); similarity between queries is to be measured using cosine between the corresponding
+vectors. We are also given a set of queries $Q$. 
+We are interested in developing a batch process to return a \emph{small}
+set of candidate neighbors for each query $q \in Q$ such that the following
+are satisfied: 1) the similarity of any returned candidate to the query $q$ is larger than a user-specified 
+similarity threshold $\tau$; 2) the set of candidates returned has a large recall. 
+Note that, although we return an approximate set of near neighbors, our requirement forces us to 
+return a candidate set that has $100\%$ precision. Our aim is to achieve a large recall, while using
+a scalable efficient algorithm.
 
-A naive exact brute force algorithm to solve the above problem: 
-1) Compute similarity between each query and all queries in the dataset. 
-2) Return all the queries as neighbors, which have similarity affinity within a similarity threshold ($\tau$).
+The exact brute force algorithm to solve the above problem would be to compute
+similarities between each $q\in Q$ and all queries in the corpus, and return 
+all pairs that have similarities higher than the threshold $\tau$. Computing similarities
+for all pairs is computationally infeasible on a single computer even if the size of $Q$ is of the order of few thousands
+and the corpus size is hundreds of millions. Even in a distributed setting such as Hadoop, the 
+resulting communication needed between machines makes this strategy impractical.
 
-This algorithm is exact as it has both $100\%$ precision and recall. 
-However, the algorithm is naive as it is not scalable for hundreds of millions of queries. 
-The reason being conducting pairwise computations between all the queries in the dataset involves 
-quadratic number of comparisons in the query dataset size. 
-For hundreds of millions of queries, it means doing petabytes of comparisons; 
-that is  computationally challenging or infeasible even in a distributed setting (such as Hadoop).
+Our aim is to empirically study a set of locality sensitive hashing techniques
+that enable us to return a set of candidate neighbors while performing
+a much smaller (theoretically \emph{sublinear}) set of comparisons.
 

### 2014-06-01 ACL2014/system.tex
section 2 edits

@@
 a much smaller (theoretically \emph{sublinear}) set of comparisons. 
+In order to tackle this scalability problem, we explore the 
+combination of distributed computation using a map-reduce platform (Hadoop) as well as
+locality sensitive hashing (\lsh) algorithms. 
+We explore a few commonly known variants of \lsh and suggest a few novel variants
+that are suitable to the map-reduce platform. 
+The methods that we propose meets the practical requirements of a real life 
+search engine backend, and demonstrates how to use locality sensitive hashing
+on a distributed platform.
 
-The motivated behind this research is to find nearest neighbors by doing a 
-\emph{small} number of comparisons (sublinear in dataset size), instead of brute force linear search. 
-In addition to \emph{small} number of comparisons, we also want to 
-return a set of neighbor candidates with a $100\%$ precision and a large recall. 
-The method we propose meet all these criterions. We do this by exploiting 
-existing research in \lshf (a.k.a., \lsh) and propose their novel variants. 
-In particular, we develop the framework of  \lsh algorithms on a distributed 
-system (e.g. Hadoop) to take advantage of its computing efficiency.
+% The motivated behind this research is to find nearest neighbors by doing a 
+% \emph{small} number of comparisons (sublinear in dataset size), instead of brute force linear search. 
+% In addition to \emph{small} number of comparisons, we also want to 
+% return a set of neighbor candidates with a $100\%$ precision and a large recall. 
+% The method we propose meet all these criterions. We do this by exploiting 
+% existing research in \lshf (a.k.a., \lsh) and propose their novel variants. 
+% In particular, we develop the framework of  \lsh algorithms on a distributed 
+% system (e.g. Hadoop) to take advantage of its computing efficiency.
 

### 2014-06-01 ACL2014/system.tex
section 3 edits

@@
 \label{sec:approach}
-We describe a distributed Hadoop framework based on \lshf (\lsh). 
-First, we present vanilla \lsh algorithm based on the seminal research of Andoni and Indyk  \shortcite{Andoni08CACM}.
-To best of our knowledge, this is the first paper that applies this algorithm to NLP applications.
+We describe a distributed \lshf framework based on map-reduce. 
+First, we present vanilla \lsh algorithm based on the seminal work of Andoni and Indyk  \shortcite{Andoni08CACM}. 
+To best of our knowledge, this is the first paper that applies this variant of locality sensitive hashing algorithms to NLP applications.
 
-This algorithm improves the existing research in \lsh and \plebf \cite{Indyk98STOC,Charikar02STOC}. 
-\plebf was applied for noun clustering \cite{ravichandran05} and speech tasks \cite {JansenASRU11,JansenIS12}. 
-Recent prior work on new variants of \plebf  \cite{goyal12Flag} for distributional similarity is a special case of Andoni and Indyk's \lsh algorithm.
+The algorithm in \cite{Andoni08CACM} improves the existing research in \lsh and \plebf (PLEB) \cite{Indyk98STOC,Charikar02STOC}. 
+PLEB was applied for noun clustering \cite{ravichandran05} and speech tasks \cite {JansenASRU11,JansenIS12}. 
+Recent prior work on new variants of PLEB \cite{goyal12Flag} for distributional similarity can be seen as 
+implementing a special case of Andoni and Indyk's \lsh algorithm.
 
-Next, we present four new variants of vanilla \lsh algorithm motivated by the research on Multi-Probe LSH \cite{LvVLDB07}. 
-A significant drawback of vanilla \lsh is the requirement for a large number of hash tables in order to achieve good recall 
-in finding nearest neighbors. 
-The goal of  \mblshf is to get significantly better recall than the vanilla \lsh by using 
-the same number of hash tables. 
+We first present four new variants of vanilla \lsh algorithm motivated by the technique of Multi-Probe LSH \cite{LvVLDB07}. 
+A significant drawback of vanilla \lsh is that it requires a large number of hash tables in order to achieve good recall 
+in finding nearest neighbors, making the algorithm memory intensive. The goal of  \mblshf 
+is to get significantly better recall than the vanilla \lsh by using the same number of hash tables.
 %The main idea behind \mblshf is to look up multiple buckets within a table that have a high probability 
@@
 \label{sec:vlsh}
-The \lsh algorithm relies on the existence of an \lsh family. Let $H$ be a family of hash functions mapping 
+The \lsh algorithm relies on the existence of an family of locality sensitive hash functions. 
+Let $H$ be a family of hash functions mapping 
  $\mathbb{R}^D$ to some universe S. For any two query terms $p$, $q$; we chose $h\in H$ uniformly at random; 
- and analyze the probability that $h(p) = h(q)$.  The family $H$ is called a \lsh family if 
+ and analyze the probability that $h(p) = h(q)$.  
+ Suppose $d$ is a distance function (cosine distance for us), 
+$R > 0$ be a distance threshold $R>0$ and $c>1$ be an approximation factor.   
+Let $P_1, P_2 \in (0, 1)$ be two probability thresholds.  
+The family $H$ of hash functions is called a $(R, cR, P_1, P_2)$ locality sensitive family if 
  it satisfies the following conditions:
-
 \begin{enumerate}
-\item $d(p,q) \leq R$, then $Pr[h(p)=h(q)] \geq P_1$ 
-\item $d(p,q) \geq cR$, then $Pr[h(p)=h(q)] \leq P_2$
+\item If $d(p,q) \leq R$, then $Pr[h(p)=h(q)] \geq P_1$, 
+\item and if $d(p,q) \geq cR$, then $Pr[h(p)=h(q)] \leq P_2$
 \end{enumerate}
-
-In above conditions, $d$ is a distance function\footnote{In this paper, we use cosine distance.}, 
-a distance threshold $R>0$ and an approximation factor $c>1$.
-
-A family is generally interesting when  $P_1>P_2$. 
+An \lsh family is generally interesting when  $P_1>P_2$. 
 However, the difference between $P_1$ and $P_2$ can be very small. 
-Given a family $H$ of hash functions with parameters ($R, cR, P_1,P_2$), 
-\lsh algorithm is devised by amplifying the gap between 
+Given a family $H$ of hash functions with parameters $(R, cR, P_1,P_2)$, 
+the \lsh algorithm is devised by amplifying the gap between 
 the two probabilities $P_1$ and $P_2$ by concatenating several functions. 
-In particular, \lsh algorithm concatenates $K$ hash functions: 
+In particular, \lsh algorithm concatenates $K$ hash functions
+to create a new hash function $g(\cdot)$ as:
 $g(q)=(h_1(q),h_2(q),\dots,h_K(q))$. 
-The larger value of $K$ leads to larger 
-gap between probabilites of collision between close queries and far queries; 
-the probabilities are $P_1^{K}$ and $P_2^{K}$ respectively. 
-The advantage of this amplification is that now the algorithm is more precise meaning 
-the probability of similar queries falling in same bucket is big; 
-and dis-similar queries falling in same bucket is small.
+A larger value of $K$ leads to larger 
+gap between probabilites of collision between close neighbors (i.e. distance less than $R$) and neighbors that are far (i.e. 
+distance more than $cR$); 
+the corresponding probabilities being $P_1^{K}$ and $P_2^{K}$ respectively. 
+This amplification ensures a high precision of the algorithm by  
+making the probability of dissimilar queries having the same hash value very small.
 

### 2014-06-01 ACL2014/system.tex
section 3 edits

@@
 
-In addition to the \lsh algorithm being precise, it needs to have large recall. 
-Instead of generating one set of hash table with index $g(q)=(h_1(q),h_2(q),\dots,h_K(q))$, 
-\lsh algorithm generates $L$ tables, $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q)))$; $\forall 1 \leq j \leq  L$.
+In order to increase the recall of the \lsh algorithm, the algorithm of Andoni et al. then uses
+$L$ hash tables, each constructed using a different $g_j(\cdot)$ function, where each 
+$g_j(\cdot)$ is defined as $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q)))$; $\forall 1 \leq j \leq  L$.
 
@@
 In this paper, we are interested in cosine similarity, and use the \lsh family defined by Charikar \shortcite{Charikar02STOC}. 
-For two queries; $p,q \in \mathbb{R}^D$, the cosine similarity is $\left( \frac{p.q}{ \| p \| \| q \| }\right)$. 
-The \lsh functions for cosine similarity is defined using sign($\alpha.p$); where $\alpha \in \mathbb{R}^D$ is a random vector. 
-Negative sign is represented as zero and positive sign as one; hence indexes of buckets in hash tables are $K$-sized bit signatures.  
-To generate $\alpha$, we exploit the prior work on 
-generating random projections \cite{Achlioptas03,LiH06} and 
-use hash functions trick to implicitly map features ($\mathbb{R}^D$) to a set of \{-1,+1\}.
-\footnote{Note, we represent our queries ($p$ and $q$) using only non-zero features.}  
+For two queries; $p,q \in \mathbb{R}^D$, the cosine similarity between them is $\left( \frac{p.q}{ \| p \| \| q \| }\right)$. 
+The \lsh functions for cosine similarity is defined as follows: if $\alpha \in \mathbb{R}^D$ is a random vector, 
+then a corresponding hash function $h_{\alpha}$ can be defined as $h_{\alpha}(p) = \mathrm{sign}(\alpha \cdot p)$.
+Typically, a negative sign is represented as $0$ and positive sign as $1$, and indices of buckets in the hash tables (i.e. the
+range of each $g_j$) are $K$ bit vectors. 
+In order to create a random vector $\alpha$, we exploit the intuition in
+\cite{Achlioptas03,LiH06} and sample each coordinate of $\alpha$ from $\{-1, +1\}$ with equal probability.
+Practically, each coordinate of $\alpha$ is generated using a hash function that maps that coordinate
+to $\{-1, +1\}$ (this is termed ``hashing trick'' in~\cite{}). 
+%\footnote{Note, we represent our queries ($p$ and $q$) using only non-zero features.}  
 This hashing trick is important and useful as we do not need to explicitly store the 
@@
 %To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
-%Our framework has three main steps: 
+%Our framework has three main steps
 %i) Generate $256$ bit signature for each query.  
@@
 %with similarity $\geq\tau$.  
-
-Vanilla \lsh has two main steps: preprocessing the data and querying the database.  
-The pseudo code written for vanilla \lsh is summarized in .
-
-In preprocessing step, the algorithm takes input as $N$ queries with an associated feature vectors. In our setting, 
-feature vector is very high dimensional and sparse; that is the clicked webpages (urls) for a given query term. 
-During preprocessing, first we generate $L\times K$ hash functions. 
-Next, we hash all queries using these hash functions to build $L$ hash tables 
+%
+Figure~\ref{algo:lsh} describes the algorithm for both creating the data structure, as well as for
+querying it. In preprocessing step, the algorithm takes as input $N$ queries along with the associated feature vectors. 
+In our setting, each query is represented using an extremely sparse and high dimensional feature vector
+that is constructed as follows: for query $q$, we take all the webpages (urls) that any user has clicked on 
+when querying for $q$. Using this representation, we then generate the 
+$L$ different hash values for each query $q$, where each such hash value is again 
+the concatenation of $K$ hash functions. These $L$ hash values per query are then used to create $L$ hash tables.
+Since the width of the index of each bucket $K$, each hash table contains at most $2^K$ buckets. 
 with each hash table containing at most $2^K$ buckets.
-There are at most $2^K$ buckets because index of each bucket: $g_j$ is $K$-widith bit index. 
-Each query term is placed in their respective buckets for all  $L$ hash tables.
+Each query term is then placed in their respective buckets for each of the $L$ hash tables.
 
@@
 
-%in Algorithm \ref{alg:vanilla-LSH}.
-
+\begin{figure}
 \fbox{
 \begin{minipage}{2.5in}
-{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors \\
+{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors 
 \begin{itemize}
@@
 
-{\bf Query:} Input is queries ($q=1,2,\dots,M$); $M$ is the number of test queries \\
+{\bf Query:} Input is queries ($q=1,2,\dots,M$); $M$ is the number of test queries
 \begin{itemize}
@@
 \end{itemize}
+
 \end{itemize}
@@
 }
+\caption{\lshf Algorithm}
+\end{figure}
 

### 2014-06-01 ACL2014/system.tex
section 3 edits

@@
 Practically, each coordinate of $\alpha$ is generated using a hash function that maps that coordinate
-to $\{-1, +1\}$ (this is termed ``hashing trick'' in~\cite{}). 
+to $\{-1, +1\}$ (this is termed ``hashing trick'' in~\cite{weinberger09hashing}). 
 %\footnote{Note, we represent our queries ($p$ and $q$) using only non-zero features.}  
@@
 %
-Figure~\ref{algo:lsh} describes the algorithm for both creating the data structure, as well as for
+Figure~\ref{alg:lsh} describes the algorithm for both creating the data structure, as well as for
 querying it. In preprocessing step, the algorithm takes as input $N$ queries along with the associated feature vectors. 
@@
 
-In querying step, for input $M$ test queries, we retrieve all the query 
-terms which appear in the buckets associated with $M$ test queries. 
-Next, compute cosine similarity between each of the retrieved terms 
-and the input test queries. Return all those queries as neighbors 
+In order to retrieve near neighbors, for each of the $M$ test queries, we first 
+retrieve all the query terms which appear in the buckets associated with each of the $M$ test queries. 
+Next, we compute cosine similarity between each of the retrieved terms 
+and the input test queries and return all those queries as neighbors 
 which are within a similarity threshold ($\tau$).
 
-In this research, we have implemented the above algorithm within the distributed setting (Hadoop).   
-In our experiments, we show that the algorithm scales to hundreds of millions of queries (see Section \ref{subsec:eval:vanillaLSH}).
+In this work, we have implemented the above algorithm in a map-reduce setting (Hadoop). 
+In Section \ref{subsec:eval:vanillaLSH}, we show that the map-reduce implmentation scales to hundreds of millions of queries.
 
@@
 \begin{minipage}{2.5in}
-{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors 
+{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
 \begin{itemize}
-\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q)))$, where $h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q)))$ are chosen at random from the \lsh family.
-\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. All queries with similar $g_j$ functions ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
+\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
+$\{h_{i,j}(q), i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
+\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
+All queries with similar $g_j$ functions ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
 \end{itemize}
 
-{\bf Query:} Input is queries ($q=1,2,\dots,M$); $M$ is the number of test queries
+{\bf Query:} $M$ test queries. Let $q$ denote a test query. 
 \begin{itemize}
@@
 \caption{\lshf Algorithm}
+\label{alg:lsh}
 \end{figure}

### 2014-06-01 ACL2014/system.tex
section 3 edits

@@
 We generate $f(q)=(h_1(q),h_2(q),\dots,h_{K/2}(q)))$ of length $k/2$. 
-Next, we define $g(q)=(f_a,f_b)$, where $1\leq a < b \leq R$. This scheme generates $L= \frac{R (R -1)}{2}$. 
+Next, we define $g(q)=(f_a,f_b)$, where $1\leq a < b \leq R$. Using such pairing, we
+can thus generate $L= \frac{R (R -1)}{2}$ hash indices. 
 This scheme requires O($K  \sqrt L$) hash functions, instead of O($KL$).    
-For rest of this paper, we use the above trick to generate $L$ hash tables with $K$-widith bit bucket-ids. 
+For rest of this paper, we use the above trick to generate $L$ hash tables with bucket indices of width $K$ bits.  
 \begin{table}
@@
 \label{sec:mblsh}
-As we discussed in Section \ref{subsec:resuseHash} that generating hash functions can be computationally expensive.  
-That is exactly one of the significant drawbacks of vanilla \lsh as it requires a large number of hash tables (large $L$) 
-in order to achieve good recall in finding nearest neighbors.
-Here, We describe four new variants of vanilla \lsh algorithm motivated by the research on \mblshf \cite{LvVLDB07}. 
-The goal of  \mblshf is to get significantly better recall than the vanilla \lsh by using 
-the same number of hash tables. The main concept behind \mblshf is to look 
-up multiple buckets within a table that have a high probability of containing the nearest neighbors of a query. 
-Note, eventhough vanila \lsh and \mblshf both have same number of hash tables ($L$); 
-\mblshf requires more number of probes as it searches in multiple buckets within a table. 
+As we discussed in Section \ref{subsec:resuseHash}, generating hash functions can be computationally expensive.
+Since the memory required by the algorithm also scales linearly with $L$, the number of hash tables, it is desirable to have a small 
+number of tables to reduce the memory footprint. The memory footprint of vanilla LSH is what makes it impractical for real applications. 
+Here, we first describe four new variants of the vanilla \lsh algorithm motivated by the intuition in
+\mblshf~\cite{LvVLDB07}. The aim of \mblshf is to obtain significantly higher recall than the vanilla \lsh while using
+the same number of hash tables. In order to achieve this, the main intuition utilized in \mblshf is that
+in addition to looking at the hash bucket that a test query $q$ falls in, it is also possible to look at the neigboring buckets
+in order to find its near neigbour candidates. \mblshf in ~\cite{LvVLDB07} suggests exploring the neighboring buckets in order of the
+Hamming distance from the bucket in which $q$ falls. The empirically show that these neighboring buckets contain the near neighbors with
+very high probability. 
+Note that, for the same number of hash tables \mblshf will require more number of probes since it searches for multiple buckets within a table. 
 The main advantage of searching in multiple buckets over generating more number of tables 
@@
 
-The original \mblshf algorithm is developed for Euclidean distance. 
-If interested in details about \mblshf algorithm for Euclidean distance, the reader is referred to \cite{LvVLDB07}. 
-Here, we propose four variants of \mblshf for cosine similarity:
+The original \mblshf algorithm is developed for Euclidean distance, the details
+are described in~\cite{LvVLDB07}. However, the Euclidean distance implementation does not immediately translate to our setting of cosine similarity. 
+For example, in generating other the list of other buckets to look into,~\cite{LvVLDB07} utilizes the distance of the hash value 
+to the boundary of the other bucket--- this
+makes sense only when the hash value is a real number and not a $0/1$ bit, as it is for us. 
+However, utilizing the same intuition, we present four variants  
+of \mblshf for cosine similarity:
 \begin{itemize}
-\item {\bf \rflipq:} The first variant is our baseline: first we compute the initial \lsh of a query q, which gives the $L$ bucket ids.  
+\item {\bf \rflipq:} The first variant is our baseline. In this, we first compute the initial \lsh of a test query $q$, which gives the $L$ bucket ids.  
 Next, we create alternate bucket ids by taking each of the $L$ bucket ids and then creating alternate candidate buckets by flipping a 
-set of coordinates randomly in the \lsh of just the query.  
-\item {\bf \rflipb:} The second variant is another baseline similar to the previous one. Instead of just flipping the bits for only the query, 
-here we flip bits for both the query and all the queries in the database. 
-\item {\bf \dflipq:} The third variant is intelligent version of first variant. Instead of randomly flipping some coordinates, 
-we devisely select a set of coordinates based on the distance of query term from the random hyperplane (hash function) 
+set of coordinates randomly in the \lsh of the test query $q$.  
+\item {\bf \rflipb:} The second variant is another baseline similar to the previous one. Instead of just flipping the bits for only the test query, 
+here we flip bits for both the test query and all the queries in the database. 
+\item {\bf \dflipq:} The third variant is a more intelligent version of first variant. Instead of randomly flipping some coordinates
+of the test query $q$, 
+we select a set of coordinates based on the distance of $q$ from the random hyperplane (hash function) 
 that was used in to create this coordinate. 
-The distance of query term from the random hyperplane is the absolute value which we get before applying the sign function on it (see Section \ref{subsec:vlsh:cosine}). 
+The distance of the test query $q$ from the random hyperplane is the absolute value which we get before applying the sign function on it 
+(see Section \ref{subsec:vlsh:cosine}), i.e. is $ \mathrm{abs}(\alpha \cdot q)$ if the random hyperplane is $\alpha$. 
 \item {\bf \dflipb:} The fourth version is similar to third one, however 
-here we flip bits for both the query and the queries in the database (intelligent version of second baseline). 
+here we flip bits for both the test query and for the queries in the database (i.e. this is the intelligent version of the second baseline). 
 \end{itemize}

### 2014-06-01 ACL2014/system.tex
section 3 edits

@@
 In this work, we have implemented the above algorithm in a map-reduce setting (Hadoop). 
-In Section \ref{subsec:eval:vanillaLSH}, we show that the map-reduce implmentation scales to hundreds of millions of queries.
+In Section \ref{subsec:eval:vanillaLSH}, we show that the map-reduce implementation scales to hundreds of millions of queries.
 
@@
 \item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
-$\{h_{i,j}(q), i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
+$\{h_{i,j}, i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
 \item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
@@
 \caption{\footnotesize{Major Notations}}
-}
+
 \label{tab:notation}

### 2014-06-01 ACL2014/system.tex
section 3 edits
updating problem statement section

@@
+\newcommand{\corpus}{$C$\xspace}
+
 \section{Problem Statement}
-We start with a corpus of user queries being represented as vectors
-over some domain (e.g. URLs); similarity between queries is to be measured using cosine between the corresponding
-vectors. We are also given a set of queries $Q$. 
-We are interested in developing a batch process to return a \emph{small}
-set of candidate neighbors for each query $q \in Q$ such that the following
-are satisfied: 1) the similarity of any returned candidate to the query $q$ is larger than a user-specified 
-similarity threshold $\tau$; 2) the set of candidates returned has a large recall. 
-Note that, although we return an approximate set of near neighbors, our requirement forces us to 
-return a candidate set that has $100\%$ precision. Our aim is to achieve a large recall, while using
+We start with user query logs \corpus having query vectors collected from 
+a commercial search engines over some domain (e.g. URLs); similarity between queries is to be measured using cosine between the corresponding
+vectors. 
+The problem we formulate here is given a set of queries $Q$ and similarity threshold $\tau$,
+we are interested in developing a batch process to return a \emph{small}
+set $T$ of candidate neighbors from \corpus for each query $q \in Q$ such that the followings
+are satisfied: 1) $T = \{ l \mid s(l, q) \geq \tau,  l \in C  \}$, where  $s(q_1, q_2)$ is a function to
+compute a similarity score between query $q_1$ and $q_2$
+; 2) $T$ achieves $100\%$ precision with ``large'' recall. 
+That is, our aim is to achieve a large recall, while using
 a scalable efficient algorithm.
@@
 The exact brute force algorithm to solve the above problem would be to compute
-similarities between each $q\in Q$ and all queries in the corpus, and return 
+similarities between each $q\in Q$ and all queries in \corpus, and return 
 all pairs that have similarities higher than the threshold $\tau$. Computing similarities
 for all pairs is computationally infeasible on a single computer even if the size of $Q$ is of the order of few thousands
-and the corpus size is hundreds of millions. Even in a distributed setting such as Hadoop, the 
-resulting communication needed between machines makes this strategy impractical.
+and the size of \corpus is hundreds of millions. Even in a distributed setting such as Hadoop, the 
+resulting communication needed between machines makes this strategy impractical.  This in turn highlights ``linear'' computational complexity is not always acceptable to a certain problem domains.
 
@@
 locality sensitive hashing (\lsh) algorithms. 
-We explore a few commonly known variants of \lsh and suggest a few novel variants
+We explore a few commonly known variants of \lsh and suggest several novel variants
 that are suitable to the map-reduce platform. 
@@
 \caption{\footnotesize{Major Notations}}
-
+}
 \label{tab:notation}

### 2014-06-01 ACL2014/system.tex
Update system.tex

@@
 are satisfied: 1) $T = \{ l \mid s(l, q) \geq \tau,  l \in C  \}$, where  $s(q_1, q_2)$ is a function to
-compute a similarity score between query $q_1$ and $q_2$
+compute a similarity score between query feature vector $q_1$ and $q_2$
 ; 2) $T$ achieves $100\%$ precision with ``large'' recall. 

### 2014-06-02 ACL2014/system.tex
small edits

@@
 \item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
-All queries with similar $g_j$ functions ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
+All queries with the same $g_j$ value ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
 \end{itemize}
@@
 Here, we first describe four new variants of the vanilla \lsh algorithm motivated by the intuition in
-\mblshf~\cite{LvVLDB07}. The aim of \mblshf is to obtain significantly higher recall than the vanilla \lsh while using
+\mblshf~\cite{LvVLDB07}. \mblshf obtains significantly higher recall than the vanilla \lsh while using
 the same number of hash tables. In order to achieve this, the main intuition utilized in \mblshf is that

### 2014-06-02 ACL2014/system.tex
small edits

@@
 in order to find its near neigbour candidates. \mblshf in ~\cite{LvVLDB07} suggests exploring the neighboring buckets in order of the
-Hamming distance from the bucket in which $q$ falls. The empirically show that these neighboring buckets contain the near neighbors with
-very high probability. 
-Note that, for the same number of hash tables \mblshf will require more number of probes since it searches for multiple buckets within a table. 
+Hamming distance from the bucket in which $q$ falls. They then empirically show that these neighboring buckets contain 
+the near neighbors with very high probability. 
+Although \mblshf is achieves a higher recall for the same number of hash tables, it will also require more number of 
+probes since it searches for multiple buckets within a table. 
 The main advantage of searching in multiple buckets over generating more number of tables 

### 2014-06-02 ACL2014/abstract.tex
updated abstract

@@
 \begin{abstract}
-Many applications from various domains such as World Wide Web, Mobile, and NLP
-rely on finding nearest neighbors given a data instance.
-Due to the very large scale
+Many applications from various domains such as web search, mobile
+browsing, and NLP rely on finding the nearest neighbors of a given
+text string from a large database.
+Due to the very large scale of data involved 
 (e.g., users' queries from commercial search engines),
-computing nearest neighbors is often required to
-understand users' intents. However, it is a non-trivial
+computing nearest neighbors is the best way to 
+%often required to
+understand users' intents. 
+However, it is a non-trivial
 task as the computational complexity grow significantly with the number of queries.
-To challenge the aforementioned problem, we exploit 
+To address this challenge, we exploit 
 \lshf (a.k.a, \lsh) methods and propose 
-novel varaints in a distributed computing environment (e.g. Hadoop). 
+novel varaints in a distributed computing environment (specifically, Hadoop). 
+We identify several optimizations which improve performance, suitable
+for deployment in very large scale settings. 
 The experimental results demonstrate our 
-proposed variants of \lsh achieve the robust performance with better recall compared with Vanilla \lsh even
-when using the same space determined by the number of hash tables .
+proposed variants of \lsh achieve the robust performance with better
+recall compared with ``vanilla'' \lsh,  even
+when using the same space determined by the number of hash tables.
 

### 2014-06-02 ACL2014/intro.tex
initial edits on intro

@@
  \section{Introduction}
-Millions of users visit commercial search engines and ``query'' 
-their interests. To provide users with high quality of services, 
+Every day, 
+hundreds of millions of users visit commercial search engines to pose
+queries on topics of their interest.  
+Such queries are typically just a few key words intended to specify
+the topic that the user has in mind. 
+To provide users with a high quality service, 
 search engines such as Bing, Google, and Yahoo require
-intelligent analysis to realize users' implicit intents, in particular taking
-advantage of large scaled query logs.  One of the key
-interesting tasks involved in learning users' implicit intents often involves 
-computing nearest neighbors (queries) for a user given query. 
+intelligent analysis to realize users' implicit intents.
+The key resource that they have to help tease out what is meant is
+their large history of requests, in the form of large scale query logs.  
+A key primitive in 
+%One of the key interesting tasks involved in 
+learning users' implicit intents is the computation of 
+nearest neighbors (queries) for a user given query. 
 Computing nearest neighbors is useful for 
@@
 finding near-duplicate queries \cite{}, spelling correction \cite{},  
-, paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 
+paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 
 and diversifying search results \cite{Song11SIGIR}.
 
-In this research, we focus on finding nearest neighbors for a given query
-from very large scaled query logs available from a commercial search engine. 
+In this paper, we focus on the problem of finding nearest neighbors
+for a given query from very large scale query logs available from a commercial search engine. 
 %In order to understand the implicit users' intent, each query is initially represented in a high dimensional feature space,
 %where each dimension corresponds to a clicked url.
+Given the importance of this question, it is important to design
+algorithms that can scale to many queries over huge logs, and allow
+online and offline computation. 
 However, computing nearest neighbors of a query 
-from large-scale query logs is a non-trivial task due to the computational complexity among hundreds of millions of  queries.
+%from large-scale query logs is a non-trivial task 
+can be very costly. 
+Naive solutions that involve a linear search of the set of possibilities
+are simply infeasible in these settings. 
+%due to the computational complexity among hundreds of millions of  queries.
 %The reason being conducting pairwise computations between a given query and all the queries in the dataset involves 
@@
 %it means doing petabytes of comparisons; that is computationally challenging or infeasible even in a distributed setting (such as Hadoop). 
-Note that even in a distributed computing environment such as Hadoop, the naive pairwise computation is not feasible from our experiments  using 2000 random queries to attempt to retrieve neighbors from the query logs consisting of hundreds of millions of queries.
+Even though distributed computing environments such as Hadoop
+make it feasible to store and search large data sets in parallel, 
+%Note that even in a distributed computing environment such as Hadoop,
+%the
+the naive pairwise computation is still infeasible. 
+The reason is that the total amount of work performed is still huge,
+and simply throwing more resources at the problem is not effective. 
+Given a log of hundreds of millions queries, most are ``far'' from a
+query of interest, and we should aim to avoid doing many ``useless''
+comparisons that confirm that queries are indeed far from it. 
+% from our experiments  using 2000 random queries to attempt to retrieve neighbors from the query logs consisting of hundreds of millions of queries.
 In other words, even though the big \textit{O} notation is denoted as linear, \textit{2000*N} comparisons are not feasible when \textit{N} reaches to hundreds of millions.
 
-In order to address the computational challenge, this paper exploits to find nearest neighbors by doing a 
+In order to address the computational challenge, this paper aims to find nearest neighbors by doing a 
 \emph{small} number of comparisons -- that is, sublinear in dataset size -- instead of brute force linear search. 
 In addition to \emph{small} number of comparisons, we aim to 
-retrieve neighboring candidates with a $100\%$ precision and a large recall.
-It is important that false positive rate (ratio of  ``incorrectly'' identifying queries as neighbors) is to be penalized more severely than false negative (ratio of missing ``true'' neighbors).
+retrieve neighboring candidates with  $100\%$ precision and high recall.
+It is important that false positive rate (ratio of  ``incorrectly'' identifying queries as neighbors) is penalized more severely than false negative (ratio of missing ``true'' neighbors).
 

### 2014-06-02 ACL2014/experiments.tex
small edits to expts

@@
 \section{Experiments}
-We evaluate our  distributed large-scale approximate similarity framework by conducting 
-several experiments on a publicly available query logs and 
-large-scale query logs sampled from a commercial search engine.
+We evaluate our  distributed large-scale approximate near neighbor framework by conducting 
+several experiments on publicly available query logs as well as a 
+large-scale query log collected from a commercial search engine.
 
 \subsection{Data}
-The public dataset that we demonstrate result on is adapted from the query logs of AOL (\aol dataset) search engine \cite{Pass06}. 
-Moreover, we show results on large-scale query logs (hundreds of millions of queries) sampled from a commercial search engine. The \dataA  
-denotes $1$\% sampled query logs from a commercial search engine, \dataB ($10$\%), and  \dataC ($100$\%). 
-Each query point has an associated feature vector, that is high dimensional and sparse. 
-Feature vector contains the  webpages (urls) that are weighted based on click through rate on the urls for the query term.  
-As a pre-processing step, we remove all those queries that have less than or equal to five clicked urls. 
-Table \ref{tab:data} summarizes the statistics of our several query-logs datasets. Our biggest dataset has $N=600$ million unique queries 
-with billions of unique urls as features.
+The public dataset that we demonstrate results on is adapted from the query logs of the AOL search engine \cite{Pass06}  (\aol dataset). 
+Moreover, we show results on a large query log (hundreds of millions of queries) sampled from a commercial search engine. 
+We started by collecting a dataset over multiple days, and containing $N=600$ million unique queries: this does not represent
+an exhaustive set of queries posed to the search engine. We then created multiple datasets from this corpus by subsampling it at various rates.
+\dataA represents a $1\%$ sample of queries from the above corpus, \dataB represents a $10\%$ sample and \dataC represents the entire corpus. 
+For each query, a high dimensional and sparse, feature vector was created over the domain of urls (the size of the domain is a few billion).   
+The feature vector of a query $q$ contains the  webpages (urls) that have received a user click for this search query $q$. The weight of 
+an url feature for a query $q$ depends on the click through rate of this url for the query $q$.  
+As a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
+Table \ref{tab:data} summarizes the statistics of our query-log datasets.
 
-{\bf Test Data:} We conduct all the experiments on 2000 random queries sampled from the query logs. 
-For evaluation, we compute the true similar candidates for all 2000 test queries by calculating cosine similarity 
-between 2000 test queries and all the queries in the dataset. In this paper, we set similarity threshold  $\tau=0.7$ 
-that means the algorithm need to retrieve candidates that have cosine similarity larger than or equal to $\tau$.
+\paragraph{Test Data}: We conduct all the experiments using $2000$ random queries sampled from the query logs as the test set of queries. 
+For evaluation, we compute the true similar candidates for all the $2000$ test queries by calculating cosine similarity 
+between each test query and all the queries in the rest of the dataset. In this paper, we set the similarity threshold  $\tau=0.7$, 
+which means that the algorithm needs to retrieve candidates that have cosine similarity larger than or equal to $0.7$.
 
@@
 \subsection{Evaluation Metrics}
-We use two metrics for evaluation: Recall and Comparisons. 
-Recall is the fraction of \emph{true} similar candidates (found in exact cosine similarity returned candidates) 
-retrieved by approximate LSH algorithms.  
-Comparisons is the average number of pairwise comparisons per query. 
-The goal of this paper is to maximize recall and minimize comparisons.
+We use two metrics for evaluation: recall and number of comparisons. 
+Recall of an LSH algorithm is the fraction of \emph{true} similar candidates (found using candidates returned by computing exact cosine similarity) 
+that is retrieved by the LSH algorithm.  
+The number of comparisons performed by an algorithm is computed as the average number of pairwise comparisons that is done per test query. 
+The goal of this paper is to maximize recall and minimize the number of comparisons.
 
@@
 \hline
-\multirow{2}{*}{$\tau$} & \multicolumn{2}{c}{\aol} & \multicolumn{2}{c}{\dataA} \\
- & Comparisons & Recall & Comparisons & Recall  \\
+\multirow{2}{*}{$\tau$}  & \multicolumn{2}{c}{\small \aol} & \multicolumn{2}{c}{\small \dataA} \\
+ & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
 \hline
@@
 \hline
-\multirow{2}{*}{L} & \multicolumn{2}{c}{\aol} & \multicolumn{2}{c}{\dataA} \\
- & Comparisons & Recall & Comparisons & Recall  \\
+\multirow{2}{*}{L} & \multicolumn{2}{c}{\small \aol} & \multicolumn{2}{c}{\small \dataA} \\
+ & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
 \hline
@@
 %$K$ & Comparisons & Recall \\
-\multirow{2}{*}{K} & \multicolumn{2}{c}{\aol} & \multicolumn{2}{c}{\dataA} \\
- & Comparisons & Recall & Comparisons & Recall  \\
+\multirow{2}{*}{K} & \multicolumn{2}{c}{\small \aol} & \multicolumn{2}{c}{\small \dataA} \\
+ &{\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}   \\
 \hline
@@
 \hline
-Data & Comparisons & Recall \\
+{\small Data} & {\small Comparisons} & {\small Recall} \\
 \hline
@@
 \hline
-$Data$ & Comparisons & Recall  & Comparisons & Recall \\
+{\small Data} & {\small Comps.} & {\small Recall}  & {\small Comps.} & {\small Recall} \\
 \hline
-\aol ($K=16$) & 155 & .75 & 405 & .86 \\
-\dataA ($K=16$) & 2980 & .76  & 7904  & .84   \\
-\dataB ($K=20$) & 1954  & .64 & 5242  & .72     \\
-\dataC ($K=24$) & 1280  & -  & 3427 & -      \\
+{\small \aol ($K=16$)} & 155 & .75 & 405 & .86 \\
+{\small \dataA ($K=16$)} & 2980 & .76  & 7904  & .84   \\
+{\small \dataB ($K=20$)} & 1954  & .64 & 5242  & .72     \\
+{\small \dataC ($K=24$)} & 1280  & -  & 3427 & -      \\
 \hline 

### 2014-06-02 ACL2014/experiments.tex
small edits to expts

@@
 For evaluation, we compute the true similar candidates for all the $2000$ test queries by calculating cosine similarity 
-between each test query and all the queries in the rest of the dataset. In this paper, we set the similarity threshold  $\tau=0.7$, 
-which means that the algorithm needs to retrieve candidates that have cosine similarity larger than or equal to $0.7$.
+between each test query and all the queries in the rest of the dataset. For most of the experiments, we set the similarity threshold  $\tau=0.7$, 
+meaning that the algorithm needs to retrieve candidates that have cosine similarity larger than or equal to $0.7$.
 
@@
 
-In the first experiment, we vary the similarity threshold parameter $\tau={0.7,0.8,0.9}$ 
-with fixed $K=16$ and $L=10$ on \aol and \dataA datasets. 
-Table \ref{tab:varyTau} shows that as expected finding near-duplicates ($0.9$) 
-is easier than nearest neighbors ($0.7$). For, rest of this paper, 
-we fix $\tau=0.7$ as we are interested in both near-duplicates and nearest-neighbors.
+In the first experiment, we vary the similarity threshold parameter $\tau$ to be in $\{0.7,0.8,0.9\}$ 
+while fixing $K=16$ and $L=10$ for the \aol and \dataA datasets. 
+Table~\ref{tab:varyTau} shows that as expected, finding near-duplicates, when $\tau=0.9$, 
+is easier than finding nearest neighbors when $\tau=0.7$. For, rest of this paper, 
+we fix $\tau=0.7$ as we are interested in both near-duplicates and nearest-neighbors for our test queries.
 
-In the second experiment, we vary $L=\{1,10,28,55\}$ with fixed $K=16$ on \aol and \dataA datasets. 
-$L$ denotes the number of hash tables and $K$ denotes the length of the index of the buckets in the table. 
-If we increase $K$ (increasing the precision to reduce false positives), we also need to 
-increase $L$ to get good recall (increasing the recall to reduce false negatives). 
+In the second experiment, we vary $L$ to be in $\{1,10,28,55\}$ while fixing $K=16$ on the \aol and \dataA datasets. 
+Recal that $L$ denotes the number of hash tables and $K$ the length of the index of the buckets in the table. 
+Increasing $K$ results in increase of the precision by reducing the false positive candidates, but 
+the $L$ also need to be correspondingly increased in order the maintain a good recall
+(i.e. reduce false negatives). 
 Table \ref{tab:varyL} shows that increasing $L$ leads to better recall, 
-however at the expense of more comparisons on both the datasets. 
-In addition, having large $L$ 
-means generating large number of random projection bits and hash tables that is 
+but at the expense of performing more comparisons on both the datasets. 
+In addition, having a large $L$ 
+means generating large number of random projection bits and hash tables which is 
 both time and memory intensive. Hence, we fix $L=10$, 
-which leads to reasonable recall with fewer comparisons.
+which leads to a reasonable recall with a tolerable number of comparisons.
 
@@
 \end{table}
-
-In the third experiment, we vary $K=\{4,8,16\}$ with fixed $L=10$ on \aol and \dataA datasets. 
+In the third experiment, we vary $K$ to be in $\{4,8,16\}$ while fixing $L=10$ on \aol and \dataA datasets. 
 As expected, Table \ref{tab:varyK} shows that increasing $K$ reduces the number of 
-comparisons and worse recall on both the datasets. This is intuitive as  
+comparisons and worsens recall on both the datasets. This is intuitive as  
 the larger value of $K$ leads to larger 
@@
 and far queries (see Section \ref{sec:vlsh}). 
-Hence, we fix $K=16$ to have fewer number of comparisons.
+Hence, we fix $K=16$ to have few number of comparisons.
 
@@
 
-In the fourth experiment, we fix $L=10$ and $K=16$ and increase the size of training data. 
-Table \ref{tab:varyData} demonstrates that as we increase the training data size, 
-the number of comparisons also increase. This result indicates that $K$   
-needs to be tuned with respect to a specific dataset, 
-as large $K$ will reduce the probability of dis-similar 
+In the fourth experiment, we fix $L=10$ and $K=16$, values that were found to be reasonable using the previous experiments, 
+and then increase the size of training data. 
+Table~\ref{tab:varyData} demonstrates that as we increase the training data size, 
+the number of comparisons done by the algorithm also increase. 
+This result indicates that $K$ needs to be tuned with respect to a specific dataset, 
+as a larger $K$ will reduce the probability of dissimilar 
 queries falling within the same bucket. 
-$K$ and $L$ can be tuned by 
-randomly sampling small set of queries.\footnote{In this paper, we randomly select 2000 queries to tune parameter $K$.}
+$K$ and $L$ can be tuned by randomly sampling small set of queries. In this paper, we randomly select $2000$ queries to tune parameter $K$.
 
-In the fifth experiment, Table \ref{tab:bestLSH} shows the best $K$ and $L$ parameter settings on different 
-sized datasets.\footnote{Recall on \dataC cannot be computed, as it was computationally intensive to find exact similar neighbors.} 
-On our biggest dataset of 600 million queries, we set $K=24$, $L=10$. These parameter settings require only 
+Table \ref{tab:bestLSH}, containing the result of our fifth experiment, shows the best $K$ and $L$ parameter settings on datasets with different 
+sizes.\footnote{Recall on \dataC the precision/recall cannot be computed, as it was computationally intensive to find exact similar neighbors.} 
+On our biggest dataset of $600$ million queries, we set $K=24$ and $L=10$. These parameter settings require on an average only 
 $464$ comparisons to find approximate nearest neighbors compared to exact cosine similarity that involves 
-brute force search over all 600 million queries in the dataset.
+brute force search over all $600$ million queries in the dataset.
 
@@
 In the second row of the Table with $F=2$, \dflipb has thirteen points better recall than \rflipb with similar number of comparisons. 
-Comparing across second row of  Table \ref{tab:query:aol} and \ref{tab:both:aol} shows that flipping the bits in both query and the dataset has better recall at the expense of more comparisons.
-This is expected as flipping both means that we can find queries at distance two (one flip in query, one flip in dataset), hence more queries in each table when we do probe.
-Note, we also compared distance based flipping with random flipping on different sized data-sets, and found distance based flipping is always significantly better in terms of recall as compared to random flipping.
+Comparing across second row of  Table \ref{tab:query:aol} and \ref{tab:both:aol} shows that flipping the bits in both query and the dataset has better 
+recall at the expense of more comparisons. This is expected as flipping both means that we can find queries at distance two (one flip in query, one flip in dataset), 
+hence more queries in each table when we do probe. Note, we also compared distance based flipping with random flipping on different sized data-sets, 
+and found distance based flipping is always significantly better in terms of recall as compared to random flipping.
 
 In the third experiment, we show the results of both variants of distance based Multi Probe that is \dflipq and \dflipb on different sized datasets. 
-Table \ref{tab:dataset:final} shows the results with parameter $L=10$, $F=2$, and data-size dependent $K$ (same settings of $K$ for different sized datasets is used as in the last experiment of Section \ref{subsec:eval:vanillaLSH}).
-As observed in the last experiment, flipping bits in both query and the dataset is significantly better in terms of recall (eight points on \dataA and \dataB) with more number of comparisons.
+Table \ref{tab:dataset:final} shows the results with parameter $L=10$, $F=2$, and data-size dependent $K$ (same settings of $K$ for different sized datasets
+is used as in the last experiment of Section \ref{subsec:eval:vanillaLSH}). As observed in the last experiment, flipping bits in both query and the dataset
+is significantly better in terms of recall (eight points on \dataA and \dataB) with more number of comparisons.
 
-In the fourth experiment, Table \ref{tab:lists} shows the qualitative results for some arbitrary queries.
-These results are found by applying our system (\dflipb with parameters $L=10$, $K=24$, and $F=2$ ) on \dataC.
-The first two columns in Table \ref{tab:lists} show that the returned approximate similar neighbors can be useful in finding related queries \cite{Jones06WWW,Jain11SIGIR}.
-The third column shows an example, where we can find several popular spell errors.
+In the fourth experiment, Table \ref{tab:lists} shows the qualitative results for some arbitrary queries. These results are found by applying our
+system (\dflipb with parameters $L=10$, $K=24$, and $F=2$ ) on \dataC. The first two columns in Table \ref{tab:lists} show that the returned approximate 
+similar neighbors can be useful in finding related queries \cite{Jones06WWW,Jain11SIGIR}. The third column shows an example, where we can find several popular spell errors. 
 The last column shows different variants of a query, where user intends to find out the ``weather in trumbull ct''. 
 Modern search engines provide a direct display with respect to ``weather'' related queries. 
-Hence, if we don't have enough evidence about a specific query being related to ``weather'', we can use queries approximately similar to it to infer that if this query is about ``weather'' or not.
+Hence, if we don't have enough evidence about a specific query being related to ``weather'', we can use queries approximately similar to it to infer that 
+if this query is about ``weather'' or not.
 

### 2014-06-02 ACL2014/intro.tex
finished pass through intro

@@
 In order to address the computational challenge, this paper aims to find nearest neighbors by doing a 
-\emph{small} number of comparisons -- that is, sublinear in dataset size -- instead of brute force linear search. 
+\emph{small} number of comparisons---that is, sublinear in the dataset size---instead of brute force linear search. 
 In addition to \emph{small} number of comparisons, we aim to 
@@
 
-The methods we propose in this paper meet all these criterions by extending existing research in \lshf 
-\cite{Indyk98STOC,Charikar02STOC,Andoni06FOCS,Andoni08CACM}  to novel variants. 
-In particular, we develop the framework of  the variants on a distributed 
-system, Hadoop by taking advantage of its distributed computing power.
+In the case of seeking exact matches for queries, effective solutions
+are based on storing values in a hash table and mapping in via hash
+functions. 
+The approximate generalization of this approach is the framework of
+\lshf, where queries are more likely to collide
+under the hash function if they are more alike, and less likely to collide
+if they are less alike. 
+The methods we propose in this paper meet our criteria by extending \lshf 
+\cite{Indyk98STOC,Charikar02STOC,Andoni06FOCS,Andoni08CACM}  in novel ways. 
+In particular, we apply the framework within a distributed 
+system, Hadoop, and take advantage of its distributed computing power.
 
-Our work includes following contributions: 
+Our work makes the following contributions: 
 \begin{enumerate}
-\item We present vanilla \lsh algorithm based on the seminal research of Andoni and Indyk  \shortcite{Andoni08CACM}.
+\item We begin with a ``vanilla'' \lsh algorithm based on the seminal
+  research of Andoni and Indyk  \shortcite{Andoni08CACM}.
  To best of our knowledge, this is the first paper that applies this algorithm to NLP applications. 
-\item We propose four novel variants of vanilla LSH motivated by the research on Multi-Probe LSH \cite{LvVLDB07}.
-We show that two of our variants achieve significantly better recall than the vanilla \lsh by using the same number of hash tables.
-The main idea behind these variants is to intelligently look up multiple buckets within a table that have a high probability of containing the nearest neighbors of a query.
+\item We propose four novel variants of vanilla LSH motivated by the
+  research on Multi-Probe LSH \cite{LvVLDB07}.  We show that two of
+  our variants achieve significantly better recall than the vanilla
+  \lsh by using the same number of hash tables. The main idea behind
+  these variants is to intelligently probe multiple ``nearby'' buckets within a table that have a high probability of containing the nearest neighbors of a query.  
 \item We present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial large-scale query logs in sublinear time.
@@
 %: Random Flipping and Query-Driven Flipping. 
-\item  We show that the applicability of our system on two real-world applications such as finding related queries and removing duplicated queries.
+\item  We show that the applicability of our system on two real-world
+  applications: finding related queries and removing (near) duplicate
+  queries.
+The system outperforms competitor methods, and is currently being
+implemented for production use within a large search provider. 
 %(Increasing  direct display coverage is related to finding related queries) and ??.

### 2014-06-02 ACL2014/system.tex
a few minor fixes suggested by Graham

@@
 the concatenation of $K$ hash functions. These $L$ hash values per query are then used to create $L$ hash tables.
-Since the width of the index of each bucket $K$, each hash table contains at most $2^K$ buckets. 
-with each hash table containing at most $2^K$ buckets.
+Since the width of the index of each bucket is $K$, each hash table contains at most $2^K$ buckets. 
 Each query term is then placed in their respective buckets for each of the $L$ hash tables.
@@
 the near neighbors with very high probability. 
-Although \mblshf is achieves a higher recall for the same number of hash tables, it will also require more number of 
+Although \mblshf is achieves a higher recall for the same number of hash tables, it will also require more 
 probes since it searches for multiple buckets within a table. 

### 2014-06-02 ACL2014/applications.tex
added missing citations in intro

--- 2014-05-31 ACL2014/applications.tex
@@
 \section{Applications}
-We show the applicability of our nearest neighbors geneated using the approximate \dbflip algorithm with parameters $L=10$, $K=24$, and $F=2$ on two well-known query understanding tasks.
+In this section, we highlight several examples that take significant advantage of  the approximate \dflip algorithm presented in this paper.
+One of the interesting examples is to understand an intent of a user's query submitted to commercial search engines. Given a user's query,
+Google, Yahoo, and Bing often delivers direct display results that summarize expected contents of the query. 
+For instance, when a query ``f stock price'' is issued  to search engines, the quick summary of the stock quote with a chart is delivered 
+to the user as the part of the search engine result page. By providing this direct display results, the users are expected to consume the right contents
+in the first result reducing chances of unnecessary clicks. However, when query "f today closing price" is issued to search engines, the three major search engines 
+fail to deliver the same direct display experience to the user query, although its query intent is strongly related to ``f stock price''. 
+Therefore, by employing the \dflip, it is straightforward to build a synonym database, which helps to trigger the same direct display among related queries.
+The other example is to remove duplicated instances in a result set. 
+When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences would be distracted from ``duplicated results.'' That is, given a set of query terms, we can apply  \dflip algorithm to build $L$ hash tables, where each hash table has $K$ width bit bucket-ids.
+This in turn allows to find ``duplicated query terms'' efficiently.
+As `duplicateness'' of among query terms typically requires ``higher'' degree of similarity than ``relatedness'', we can learn $\tau$ from training samples.
+The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.

### 2014-06-02 ACL2014/intro.tex
added missing citations in intro

@@
 finding related queries \cite{Jones06WWW,Jain11SIGIR,Song12WSDM}, 
-finding near-duplicate queries \cite{}, spelling correction \cite{},  
+finding near-duplicate queries \cite{leeCIKM11}, spelling correction \cite{ahmadEMNLP05,liSIGIR12},  
 paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 

### 2014-06-03 ACL2014/abstract.tex
Updated experiments, discussion

@@
 Many applications from various domains such as web search, mobile
-browsing, and NLP rely on finding the nearest neighbors of a given
+browsing, and Natural Language Processing 
+rely on finding the nearest neighbors of a given
 text string from a large database.
@@
 However, it is a non-trivial
-task as the computational complexity grow significantly with the number of queries.
+task as the computational complexity grow 
+significantly with the number of queries.
 To address this challenge, we exploit 

### 2014-06-03 ACL2014/applications.tex
Updated experiments, discussion

@@
 \section{Applications}
-In this section, we highlight several examples that take significant advantage of  the approximate \dflip algorithm presented in this paper.
+In this section, we highlight several examples that take significant advantage of  the approximate \dflipb algorithm presented in this paper.
 One of the interesting examples is to understand an intent of a user's query submitted to commercial search engines. Given a user's query,
-Google, Yahoo, and Bing often delivers direct display results that summarize expected contents of the query. 
+Bing, Google, and Yahoo often delivers direct display results that summarize expected contents of the query. 
 For instance, when a query ``f stock price'' is issued  to search engines, the quick summary of the stock quote with a chart is delivered 
@@
 The other example is to remove duplicated instances in a result set. 
-When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences would be distracted from ``duplicated results.'' That is, given a set of query terms, we can apply  \dflip algorithm to build $L$ hash tables, where each hash table has $K$ width bit bucket-ids.
-This in turn allows to find ``duplicated query terms'' efficiently.
-As `duplicateness'' of among query terms typically requires ``higher'' degree of similarity than ``relatedness'', we can learn $\tau$ from training samples.
+When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences would be distracted from ``duplicated results.'' 
+That is, given a set of query terms, we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
+to find ``duplicated query terms'' efficiently.
+As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity (relatively easier problem) than ``relatedness'', we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples.
 The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.

### 2014-06-03 ACL2014/discussion.tex
Updated experiments, discussion

@@
 \label{sec:discuss}
-%In this paper, we demonstrated the effectiveness of our p
+In this section, we highlight several examples that take significant advantage of  the approximate \dflipb algorithm presented in this paper.
+One of the interesting examples is to understand an intent of a user's query submitted to commercial search engines. Given a user's query,
+Bing, Google, and Yahoo often delivers direct display results that summarize expected contents of the query. 
+For instance, when a query ``f stock price'' is issued  to search engines, the quick summary of the stock quote with a chart is delivered 
+to the user as the part of the search engine result page. By providing this direct display results, the users are expected to consume the right contents
+in the first result reducing chances of unnecessary clicks. However, when query "f today closing price" is issued to search engines, the three major search engines 
+fail to deliver the same direct display experience to the user query, although its query intent is strongly related to ``f stock price''. 
+Therefore, by employing the \dflipb, it is straightforward to build a synonym database, which helps to trigger the same direct display among related queries.
+
+The other example is to remove duplicated instances in a result set. 
+When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences would be distracted from ``duplicated results.'' 
+That is, given a set of query terms, we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
+to find ``duplicated query terms'' efficiently.
+As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity (relatively easier problem) than ``relatedness'', we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples.
+The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.

### 2014-06-03 ACL2014/experiments.tex
Updated experiments, discussion

@@
 large-scale query log collected from a commercial search engine.
+
+\begin{table}
+\centering
+\begin{tabular}{|c|r|r|}
+\hline
+Data & $N$ & $D$  \\ 
+\hline
+\aol &  $0.3 \times 10^6$  & $0.7 \times 10^6$ \\
+\dataA & $6 \times 10^6$  & $66 \times 10^6$ \\
+\dataB & $62 \times 10^6$  & $464 \times 10^6$ \\
+\dataC &  $617 \times 10^6$  & $ 2.4 \times 10^9$  \\
+\hline 
+ \end{tabular}
+\caption{\footnotesize{Query-logs statistics}}
+\label{tab:data}
+\end{table}
 
@@
 
-\begin{table}
-\centering
-\begin{tabular}{|c|r|r|}
-\hline
-Data & $N$ & $D$  \\ 
-\hline
-\aol &  $0.3 \times 10^6$  & $0.7 \times 10^6$ \\
-\dataA & $6 \times 10^6$  & $66 \times 10^6$ \\
-\dataB & $62 \times 10^6$  & $464 \times 10^6$ \\
-\dataC &  $617 \times 10^6$  & $ 2.4 \times 10^9$  \\
-\hline 
- \end{tabular}
-\caption{\footnotesize{Query-logs statistics}}
-\label{tab:data}
-\end{table}
-
 \subsection{Evaluation Metrics}
@@
 \hline
-\multirow{2}{*}{$\tau$}  & \multicolumn{2}{c}{\small \aol} & \multicolumn{2}{c}{\small \dataA} \\
+\multirow{2}{*}{$\tau$}  & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
  & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
@@
 In the second experiment, we vary $L$ to be in $\{1,10,28,55\}$ while fixing $K=16$ on the \aol and \dataA datasets. 
-Recal that $L$ denotes the number of hash tables and $K$ the length of the index of the buckets in the table. 
+Recal that $L$ denotes the number of hash tables and $K$ is the width of the index of the buckets in the table. 
 Increasing $K$ results in increase of the precision by reducing the false positive candidates, but 
@@
 \hline
-\multirow{2}{*}{L} & \multicolumn{2}{c}{\small \aol} & \multicolumn{2}{c}{\small \dataA} \\
+\multirow{2}{*}{L} & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
  & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
@@
 %$K$ & Comparisons & Recall \\
-\multirow{2}{*}{K} & \multicolumn{2}{c}{\small \aol} & \multicolumn{2}{c}{\small \dataA} \\
+\multirow{2}{*}{K} & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
  &{\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}   \\
@@
 
-\subsection{Evaluating Multi-Probe LSH}
-\label{subsec:eval:multiProbeLSH}
-In the first experiment, we compare flipping the bits in query only. 
-We evaluate two approaches: \rflipq and \dflipq.
-We can make several observations from Table \ref{tab:query:aol}: 1) As expected, increasing the number of flips improve recall at expense of more comparisons for both \dflipq and \rflipq.
-2) Our results show that \dflipq has significantly better recall than \rflipq with similar number of comparisons.
-In second row of the table with $F=2$, \dflipq has nine points better recall than \rflipq.
-
-In the second experiment, we compare flipping the bits in both query and the dataset. 
-We can make similar observations from Table \ref{tab:both:aol} as made in the first experiment. 
-In the second row of the Table with $F=2$, \dflipb has thirteen points better recall than \rflipb with similar number of comparisons. 
-Comparing across second row of  Table \ref{tab:query:aol} and \ref{tab:both:aol} shows that flipping the bits in both query and the dataset has better 
-recall at the expense of more comparisons. This is expected as flipping both means that we can find queries at distance two (one flip in query, one flip in dataset), 
-hence more queries in each table when we do probe. Note, we also compared distance based flipping with random flipping on different sized data-sets, 
-and found distance based flipping is always significantly better in terms of recall as compared to random flipping.
-
-In the third experiment, we show the results of both variants of distance based Multi Probe that is \dflipq and \dflipb on different sized datasets. 
-Table \ref{tab:dataset:final} shows the results with parameter $L=10$, $F=2$, and data-size dependent $K$ (same settings of $K$ for different sized datasets
-is used as in the last experiment of Section \ref{subsec:eval:vanillaLSH}). As observed in the last experiment, flipping bits in both query and the dataset
-is significantly better in terms of recall (eight points on \dataA and \dataB) with more number of comparisons.
-
-In the fourth experiment, Table \ref{tab:lists} shows the qualitative results for some arbitrary queries. These results are found by applying our
-system (\dflipb with parameters $L=10$, $K=24$, and $F=2$ ) on \dataC. The first two columns in Table \ref{tab:lists} show that the returned approximate 
-similar neighbors can be useful in finding related queries \cite{Jones06WWW,Jain11SIGIR}. The third column shows an example, where we can find several popular spell errors. 
-The last column shows different variants of a query, where user intends to find out the ``weather in trumbull ct''. 
-Modern search engines provide a direct display with respect to ``weather'' related queries. 
-Hence, if we don't have enough evidence about a specific query being related to ``weather'', we can use queries approximately similar to it to infer that 
-if this query is about ``weather'' or not.
-
-% paraphrasing \cite{ganitkevitch13Paraphrase}
-% maybe include deduplication results
-
 \begin{table}
@@
 \hline
-Method & \multicolumn{2}{c}{\rflipq} & \multicolumn{2}{c}{\dflipq}   \\
+Method & \multicolumn{2}{c|}{\rflipq} & \multicolumn{2}{c|}{\dflipq}   \\
 \hline
@@
 2 & 159 & .66 &  {\it155} & {\bf .75}  \\
-5 &  311 & .70 &  {\it 303} & {\bf .79}  \\
+5 &  311 & .70 &  303 &  .79  \\
+10 & 557  & .75 &  552 &  .81  \\
+16 & 839   & .82 &  839 &  .82  \\
 \hline 
@@
 \hline
-Method & \multicolumn{2}{c}{\rflipb} & \multicolumn{2}{c}{\dflipb}   \\
+Method & \multicolumn{2}{c|}{\rflipb} & \multicolumn{2}{c|}{\dflipb}   \\
 \hline
@@
 5 &  1557 & .86  & 1475 & .93     \\
+10 &  4138 & .94 & 4059 & .96     \\
+16 &  5922 & .96 & 5922 & .96     \\
 \hline 
@@
  }
-\caption{\footnotesize{Flipping the bits in both the query and the dataset with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
+\caption{\footnotesize{Flipping the bits in both the query and the database with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
 \label{tab:both:aol}
@@
 \hline
-Method & \multicolumn{2}{c}{\dflipq} & \multicolumn{2}{c}{\dflipb}   \\
+Method & \multicolumn{2}{c|}{\dflipq} & \multicolumn{2}{c|}{\dflipb}   \\
 \hline
@@
 \end{table*}
+
+\subsection{Evaluating Multi-Probe LSH}
+\label{subsec:eval:multiProbeLSH}
+In the first experiment, we compare flipping the bits in query only. 
+We evaluate two approaches: \rflipq and \dflipq.
+We can make several observations from Table \ref{tab:query:aol}: 1) As expected, increasing the number of flips improve recall at expense of more comparisons for both \dflipq and \rflipq.
+2) The last row of the Table \ref{tab:query:aol} shows that once we flip all the $K$ bits ($F=16$),  \dflipq and \rflipq converge to the same algorithm.
+3) Our results show that \dflipq has significantly better recall than \rflipq with similar number of comparisons.
+In second row of the table with $F=2$, \dflipq has nine points better recall than \rflipq.
+
+In the second experiment, we compare flipping the bits in both query and the database. 
+We can make similar observations from Table \ref{tab:both:aol} as made in the first experiment. 
+In the second row of the Table with $F=2$, \dflipb has thirteen points better recall than \rflipb with similar number of comparisons. 
+Comparing across second row of  Table \ref{tab:query:aol} and \ref{tab:both:aol} shows that flipping the bits in both query and the database has better 
+recall at the expense of more comparisons. This is expected as flipping both means that we can find queries at distance two (one flip in query, one flip in database), 
+hence more queries in each table when we probe. Note, we also compared distance based flipping with random flipping on different sized data-sets, 
+and found that distance based flipping is always significantly better in terms of recall as compared to random flipping.\footnote{Due to limited space, we omit those results.}
+
+We select $F=2$ as the best parameter setting with goal of maximizing recall by restricting comparisons to minimum.
+For better recall at expense of more comparisons, $F=5$ can also be selected.
+However, results in Table \ref{tab:query:aol} and \ref{tab:both:aol} indicate that $F>5$ does \emph{not} increase recall significantly and at the same time leads to more number of comparisons.
+
+In the third experiment, we show the results of both variants of distance based Multi Probe that is \dflipq and \dflipb on different sized datasets. 
+Table \ref{tab:dataset:final} shows the results with parameter $L=10$, $F=2$, and data-size dependent $K$ (same settings of $K$ for different sized datasets
+as used in the last experiment of Section \ref{subsec:eval:vanillaLSH}).  As observed in the last experiment, flipping bits in both query and the database
+is significantly better in terms of recall with more number of comparisons. The second and third row of the table respectively 
+shows that flipping bits in both query and the database has eight points better recall on both \dataA and \dataB 
+datasets. With the goal of maximizing recall with some extra comparisons, we select \dflipb as our final algorithm. 
+\dflipb maximizes recall with small number of tables and comparisons. 
+On our entire corpus (\dataC) with hundreds of millions of queries, 
+\dflipb only requires $3,427$ comparisons compared to hundreds of millions of comparisons by exact brute force algorithm.  
+\dflipb returns $9$ neighbors on average per given query; averaged over $2000$ random test 
+queries.\footnote{As many queries can be long, hence such queries only have few neighbors.}
+
+In the fourth experiment, Table \ref{tab:lists} shows the qualitative results for some arbitrary queries. These results are found by applying our
+system (\dflipb with parameters $L=10$, $K=24$, and $F=2$ ) on \dataC. The second column in Table \ref{tab:lists} shows that the returned approximate 
+similar neighbors can be useful in finding related queries \cite{Jones06WWW,Jain11SIGIR}. 
+The third column shows an example, where we can find several popular spellling errors. 
+The first and last column show examples of near-duplicate queries \cite{leeCIKM11}.
+
+%different variants of a query, where user intends to find out the ``weather in trumbull ct''. 
+%Modern search engines provide a direct display with respect to ``weather'' related queries. 
+%Hence, if we don't have enough evidence about a specific query being related to ``weather'', we can use queries approximately similar to it to infer that 
+%if this query is about ``weather'' or not.
+
+% paraphrasing \cite{ganitkevitch13Paraphrase}
+% maybe include deduplication results

### 2014-06-03 ACL2014/intro.tex
Updated experiments, discussion

--- 2014-06-02 ACL2014/intro.tex
@@
 finding related queries \cite{Jones06WWW,Jain11SIGIR,Song12WSDM}, 
-finding near-duplicate queries \cite{}, spelling correction \cite{},  
-paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 
-and diversifying search results \cite{Song11SIGIR}.
+finding near-duplicate queries \cite{leeCIKM11}, spelling correction \cite{ahmadEMNLP05,liSIGIR12},  
+and diversifying search results \cite{Song11SIGIR}; and many Natural Language Processing (NLP) tasks   
+such as paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 
+distributional similarity \cite{ravichandran05,agirre09,turneyVector10}, and creating sentiment lexicons from large-scale Web data \cite{velikovich10}.
 
@@
 %: Random Flipping and Query-Driven Flipping. 
-\item  We show that the applicability of our system on two real-world
+\item  We discuss the applicability of our framework on two real-world
   applications: finding related queries and removing (near) duplicate
-  queries.
-The system outperforms competitor methods, and is currently being
+  queries. The algorithms presented in this paper are currently being
 implemented for production use within a large search provider. 
@@
 %points $q_1,q_2,\dots,q_n$, each of them is a search-query. 
-
 %Spelling {grouping mis-spellings in same group}

### 2014-06-03 ACL2014/system.tex
Updated experiments, discussion

@@
 
-\section{Approach}
+\section{Proposed Approach}
 \label{sec:approach}
@@
 
-The algorithm in \cite{Andoni08CACM} improves the existing research in \lsh and \plebf (PLEB) \cite{Indyk98STOC,Charikar02STOC}. 
+The algorithm in Andoni and Indyk \shortcite{Andoni08CACM} improves the existing research in \lsh and \plebf (PLEB) \cite{Indyk98STOC,Charikar02STOC}. 
 PLEB was applied for noun clustering \cite{ravichandran05} and speech tasks \cite {JansenASRU11,JansenIS12}. 
@@
 $g_j(\cdot)$ is defined as $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q)))$; $\forall 1 \leq j \leq  L$. 
+We list the major notations of \lsh in Table \ref{tab:notation}.
+
+\begin{table}
+\centering
+{
+\small \addtolength{\tabcolsep}{-4.5pt}
+\begin{tabular}{ll}
+\hline
+\hline
+ \textbf{Symbol} &  \textbf{Description} \\
+\hline 
+$N$ & \# of query terms \\
+$D$ & \# of features i.e. all clicked unique urls \\
+\hline
+\multirow{3}{*}{$K$} & \# of hash functions concatenated together \\ 
+   & $g(q)=(h_1(q),h_2(q),\dots,h_k(q)))$ \\ 
+	 & to generate the index of a table \\
+\hline
+ \multirow{2}{*}{$L$} & \# of tables generated independently \\ 
+	  &  with $g_j(q)$ index, $\forall 1 \leq j \leq  L$  \\
+\hline
+$F$ & \# of bits flipped, $\forall 1 \leq j \leq  L$   \\
+$\tau$ & $\tau$ threshold \\
+Recall & fraction of similar candidates retrieved \\
+Comparisons & Avg \# of pairwise comparisons per query  \\
+\hline 
+\end{tabular}
+\caption{\footnotesize{Major Notations}}
+\label{tab:notation}
+}
+\end{table}
 
 %Recall = $1-(1-P_1^{K})^{L}$
+
+\begin{figure}[ht]
+\small
+\fbox{
+\begin{minipage}{2.5in}
+{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
+\begin{itemize}
+\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
+$\{h_{i,j}, i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
+\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
+All queries with the same $g_j$ value ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
+\end{itemize}
+
+{\bf Query:} $M$ test queries. Let $q$ denote a test query. 
+\begin{itemize}
+\item For each $j=1,2,\dots,L$
+\begin{itemize}
+\item Retrieve all the queries from the bucket with $g_j(q)$ function as the index of the bucket 
+\item Compute cosine similarity between query q and all the retrieved queries. Return all the queries which have similarity affinity within a similarity threshold ($\tau$). 
+\end{itemize}
+
+\end{itemize}
+\end{minipage}
+}
+\caption{\lshf Algorithm}
+\label{alg:lsh}
+\end{figure}
 
@@
 the concatenation of $K$ hash functions. These $L$ hash values per query are then used to create $L$ hash tables.
-Since the width of the index of each bucket is $K$, each hash table contains at most $2^K$ buckets. 
+Since the width of the index of each bucket is $K$ with each coordinate being $0/1$ bit, each hash table contains at most $2^K$ buckets. 
 Each query term is then placed in their respective buckets for each of the $L$ hash tables.
@@
 In Section \ref{subsec:eval:vanillaLSH}, we show that the map-reduce implementation scales to hundreds of millions of queries.
-
-\begin{figure}
-\fbox{
-\begin{minipage}{2.5in}
-{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
-\begin{itemize}
-\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
-$\{h_{i,j}, i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
-\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
-All queries with the same $g_j$ value ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
-\end{itemize}
-
-{\bf Query:} $M$ test queries. Let $q$ denote a test query. 
-\begin{itemize}
-\item For each $j=1,2,\dots,L$
-\begin{itemize}
-\item Retrieve all the queries from the bucket with $g_j(q)$ function as the index of the bucket 
-\item Compute cosine similarity between query q and all the retrieved queries. Return all the queries which have similarity affinity within a similarity threshold ($\tau$). 
-\end{itemize}
-
-\end{itemize}
-\end{minipage}
-}
-\caption{\lshf Algorithm}
-\label{alg:lsh}
-\end{figure}
 
@@
 For rest of this paper, we use the above trick to generate $L$ hash tables with bucket indices of width $K$ bits.
-\begin{table}
-\centering
-{
-\small \addtolength{\tabcolsep}{-4.5pt}
-\begin{tabular}{ll}
-\hline
-\hline
- \textbf{Symbol} &  \textbf{Description} \\
-\hline 
-$N$ & \# of query terms \\
-$D$ & \# of features i.e. all clicked unique urls \\
-\hline
-\multirow{3}{*}{$K$} & \# of hash functions concatenated together \\ 
-   & $g(q)=(h_1(q),h_2(q),\dots,h_k(q)))$ \\ 
-	 & to generate the index of a table \\
-\hline
- \multirow{2}{*}{$L$} & \# of tables generated independently \\ 
-	  &  with $g_j(q)$ index, $\forall 1 \leq j \leq  L$  \\
-\hline
-$F$ & \# of bits flipped, $\forall 1 \leq j \leq  L$   \\
-$\tau$ & $\tau$ threshold \\
-Recall & fraction of similar candidates retrieved \\
-Comparisons & Avg \# of pairwise comparisons per query  \\
-\hline 
-\end{tabular}
-\caption{\footnotesize{Major Notations}}
-}
-\label{tab:notation}
-\end{table}
 

### 2014-06-03 ACL2014/relatedwork.tex
related work

\section{Related Work}
Locality sensitive hashing is a very well studied algorithmic tool, that has found practical uses too. 
In processing large text corpora, however, LSH algorithms have been less used, primarily because of their
still significant memory requirements. Recent work by~\cite{zadeh2013dimension} developed a modification of LSH algorithm, for 
the Jaccard distance metric, that scales to very large text corpora by virtue of being implemented on a map-reduce, 
and by using clever sampling schemes in order to reduce the communication cost. Our work is for the cosine similarity metric, 
and uses bit flipping in a distributed manner to reduce the number of hash tables in LSH and hence the memory. 
Other innovations to LSH methods in the text corpora analysis domain include developing methods to compute
LSH signatures in an online manner~\cite{van2010online}, and using reservoir sampling to compute the signatures~\cite{van2011efficient}.

### 2014-06-03 ACL2014/discussion.tex
Updated bin

@@
 The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.
+
+We first described the existing ``vanilla'' \lsh algorithm. It is the first paper according to 
+best of our knowledge that applies this algorithm to NLP applications. 
+Next, we poposed four novel variants of vanilla \lsh. Two of our variants achieve 
+significantly better recall than the vanilla LSH by using the same number of hash tables. 
+We present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial large-scale query logs (consisting of hundreds of millions of queries) in sublinear time.

### 2014-06-03 ACL2014/discussion.tex
spelling fixes

@@
 to find ``duplicated query terms'' efficiently.
-As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity (relatively easier problem) than ``relatedness'', we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples.
+As ``duplicates'' among query terms typically requires ``higher'' degree of similarity (relatively easier problem) than ``relatedness'', we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples.
 The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.
@@
 best of our knowledge that applies this algorithm to NLP applications. 
-Next, we poposed four novel variants of vanilla \lsh. Two of our variants achieve 
+Next, we proposed four novel variants of vanilla \lsh. Two of our variants achieve 
 significantly better recall than the vanilla LSH by using the same number of hash tables. 

### 2014-06-03 ACL2014/experiments.tex
spelling fixes

@@
 In the second experiment, we vary $L$ to be in $\{1,10,28,55\}$ while fixing $K=16$ on the \aol and \dataA datasets. 
-Recal that $L$ denotes the number of hash tables and $K$ is the width of the index of the buckets in the table. 
+Recall that $L$ denotes the number of hash tables and $K$ is the width of the index of the buckets in the table. 
 Increasing $K$ results in increase of the precision by reducing the false positive candidates, but 
@@
 the larger value of $K$ leads to larger 
-gap between probabilites of collision between close queries 
+gap between probabilities of collision between close queries 
 and far queries (see Section \ref{sec:vlsh}). 
@@
 similar neighbors can be useful in finding related queries \cite{Jones06WWW,Jain11SIGIR}. 
-The third column shows an example, where we can find several popular spellling errors. 
+The third column shows an example, where we can find several popular spelling errors. 
 The first and last column show examples of near-duplicate queries \cite{leeCIKM11}.

### 2014-06-03 ACL2014/system.tex
Updated bin
spelling fixes

@@
 A larger value of $K$ leads to larger 
-gap between probabilites of collision between close neighbors (i.e. distance less than $R$) and neighbors that are far (i.e. 
+gap between probabilities of collision between close neighbors (i.e. distance less than $R$) and neighbors that are far (i.e. 
 distance more than $cR$); 
@@
 \begin{figure}[ht]
-\small
+%\small
 \fbox{
@@
 the same number of hash tables. In order to achieve this, the main intuition utilized in \mblshf is that
-in addition to looking at the hash bucket that a test query $q$ falls in, it is also possible to look at the neigboring buckets
-in order to find its near neigbour candidates. \mblshf in ~\cite{LvVLDB07} suggests exploring the neighboring buckets in order of the
+in addition to looking at the hash bucket that a test query $q$ falls in, it is also possible to look at the neighboring buckets
+in order to find its near neighbor candidates. \mblshf in ~\cite{LvVLDB07} suggests exploring the neighboring buckets in order of the
 Hamming distance from the bucket in which $q$ falls. They then empirically show that these neighboring buckets contain 

### 2014-06-03 ACL2014/discussion.tex
conclusions

--- 2014-06-03 ACL2014/discussion.tex
@@
 \label{sec:discuss}
-In this section, we highlight several examples that take significant advantage of  the approximate \dflipb algorithm presented in this paper.
-One of the interesting examples is to understand an intent of a user's query submitted to commercial search engines. Given a user's query,
-Bing, Google, and Yahoo often delivers direct display results that summarize expected contents of the query. 
+In this section, we highlight several applications that take significant advantage of the approximate \dflipb algorithm presented in this paper.
+One of the interesting applications of the near-neighbor finding is to understand specific intents behind the user query. 
+Given a user's query, Bing, Google, and Yahoo often delivers direct display results that summarize expected contents of the query. 
 For instance, when a query ``f stock price'' is issued  to search engines, the quick summary of the stock quote with a chart is delivered 
-to the user as the part of the search engine result page. By providing this direct display results, the users are expected to consume the right contents
-in the first result reducing chances of unnecessary clicks. However, when query "f today closing price" is issued to search engines, the three major search engines 
+to the user as the part of the search engine result page. 
+Such direct display results are expected to reduce the number of unnecessary clicks by providing the user with the appropriate content early on. 
+However, when the query "f today closing price" is issued to search engines, the three major search engines 
 fail to deliver the same direct display experience to the user query, although its query intent is strongly related to ``f stock price''. 
-Therefore, by employing the \dflipb, it is straightforward to build a synonym database, which helps to trigger the same direct display among related queries.
+By employing an algorithm similar to \dflipb, we can build a synonym database, 
+which will help trigger the same direct display among related queries.
 
-The other example is to remove duplicated instances in a result set. 
-When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences would be distracted from ``duplicated results.'' 
+Yet another application is removing duplicated instances in a result set. 
+When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences 
+would be distracted from ``duplicated results.'' 
 That is, given a set of query terms, we can apply  \dflipb algorithm to build a lookup table of near-duplicates 

### 2014-06-03 ACL2014/experiments.tex
updating experiments

--- 2014-06-03 ACL2014/experiments.tex
@@
 \section{Experiments}
-We evaluate our  distributed large-scale approximate near neighbor framework by conducting 
-several experiments on publicly available query logs as well as a 
-large-scale query log collected from a commercial search engine.
+In this section, we illustrate experimental results to evaluate our distributed neighbor search framework.
+Our experiments are conducted on publicly available query logs collected from the AOL search engine~\cite{Pass06} as well as a 
+large-scale query log from a commercial search engine.
 
@@
 \subsection{Data}
-The public dataset that we demonstrate results on is adapted from the query logs of the AOL search engine \cite{Pass06}  (\aol dataset). 
-Moreover, we show results on a large query log (hundreds of millions of queries) sampled from a commercial search engine. 
-We started by collecting a dataset over multiple days, and containing $N=600$ million unique queries: this does not represent
-an exhaustive set of queries posed to the search engine. We then created multiple datasets from this corpus by subsampling it at various rates.
-\dataA represents a $1\%$ sample of queries from the above corpus, \dataB represents a $10\%$ sample and \dataC represents the entire corpus. 
+The first data set is the one made avialble to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
+In addition, we perform evaluations using a large query log 
+%(hundreds of millions of queries) 
+from a commercial search engine, denoted as Qlogs. 
+As Qlogs typically reaches to hundres of millions of queries over multiple days (i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive set of queries posed to the search engine.}.) We then generated multiple datasets from Qlogs by sampling at various size rates.
+\dataA represents a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs.
 For each query, a high dimensional and sparse, feature vector was created over the domain of urls (the size of the domain is a few billion).   

### 2014-06-03 ACL2014/discussion.tex

--- 2014-06-03 ACL2014/discussion.tex
@@
-\section{Discussion and Conclusion}
+\section{Discussion}
 \label{sec:discuss}
-In this section, we highlight several applications that take significant advantage of the approximate \dflipb algorithm presented in this paper.
+In this section, we highlight several applications that can take significant advantage of the approximate \dflipb algorithm presented in this paper.
 One of the interesting applications of the near-neighbor finding is to understand specific intents behind the user query. 
@@
 
-Yet another application is removing duplicated instances in a result set. 
-When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences 
-would be distracted from ``duplicated results.'' 
-That is, given a set of query terms, we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
-to find ``duplicated query terms'' efficiently.
-As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity (relatively easier problem) than ``relatedness'', we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples.
-The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.
+Yet another application is removing duplicated instances in a set of suggested results. 
+When a query set is retrieved from a repository and presented to users, it is important to remove similar queries
+from the set so that the user is not distracted by duplicated results. Given a set of
+we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
+in order to find the ``duplicated query terms'' efficiently. 
+As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity 
+(relatively easier problem) than ``relatedness'', 
+we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples. 
+The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples-- ``trumbull weather ct'' and ``weather in trumbull ct''.
 
-We first described the existing ``vanilla'' \lsh algorithm. It is the first paper according to 
-best of our knowledge that applies this algorithm to NLP applications. 
-Next, we poposed four novel variants of vanilla \lsh. Two of our variants achieve 
+\section{Conclusion}
+\label{sec:conclusion}
+To the best of our knowledge, this is the first paper that applies
+the vanilla \lsh algorithm of Andoni et al. to the NLP domain. 
+We also proposed four novel variants of \lsh that are aimed to reduce the number 
+of hash tables used. Two of our variants achieve 
 significantly better recall than the vanilla LSH by using the same number of hash tables. 
-We present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial large-scale query logs (consisting of hundreds of millions of queries) in sublinear time.
+We also present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial 
+large-scale query logs (consisting of hundreds of millions of queries) in sublinear time.

### 2014-06-03 ACL2014/relatedwork.tex

@@
 \section{Related Work}
-Locality sensitive hashing is a very well studied algorithmic tool, that has found practical uses too. 
-In processing large text corpora, however, LSH algorithms have been less used, primarily because of their
-still significant memory requirements. Recent work by~\cite{zadeh2013dimension} developed a modification of LSH algorithm, for 
+
+There has been many papers in last decade that have focused on 
+approximate, streaming, and randomized algorithms on many NLP problems. 
+Prior work on \lsh for noun clustering \cite{ravichandran05} applied 
+original version of \lsh based on \plebf (PLEB) \cite{Indyk98STOC,Charikar02STOC}. 
+The disadvantage of original \lsh algorithm is that it involves generating large number of permutations ($L=1000$, 
+generating permutation is similar to generating more tables)
+and sorting bit vectors of large width ($K=3000$). 
+To address that issue, Goyal et al. \cite{goyal12Flag} proposed a new variant of PLEB that
+is faster than the original \lsh algorithm but that still requires large number of permutations 
+($L=1000$). In addition, their work can be seen as an implementing a special case of Andoni and Indyk's \lsh algorithm.
+
+The next major difference between our research and existing work is that the 
+existing work deals with approximating cosine similarity by Hamming distance  
+\cite{ravichandran05,vandurme-lall:2010:Short,vandurme-lall:2011:Short,goyal12Flag}. 
+In that problem setting, the goal is to minimize both false positives and negatives. 
+In our work, we focus on minimizing false negatives with zero tolerance for false positives.
+
+\cite{zadeh2013dimension} developed a distributed version of the LSH algorithm, for 
 the Jaccard distance metric, that scales to very large text corpora by virtue of being implemented on a map-reduce, 
@@
 and uses bit flipping in a distributed manner to reduce the number of hash tables in LSH and hence the memory.
-Other innovations to LSH methods in the text corpora analysis domain include developing methods to compute
-LSH signatures in an online manner~\cite{van2010online}, and using reservoir sampling to compute the signatures~\cite{van2011efficient}.

### 2014-06-03 ACL2014/experiments.tex
updating experiment section

@@
 In addition, we perform evaluations using a large query log 
-%(hundreds of millions of queries) 
 from a commercial search engine, denoted as Qlogs. 
@@
 \dataA represents a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs.
-For each query, a high dimensional and sparse, feature vector was created over the domain of urls (the size of the domain is a few billion).   
-The feature vector of a query $q$ contains the  webpages (urls) that have received a user click for this search query $q$. The weight of 
+For each query, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion).   
+Specifically, each dimension in the feature vector of a query $q$ corresponds to a webpage (urls) that have received a user click for $q$. The weight of 
 an url feature for a query $q$ depends on the click through rate of this url for the query $q$.  

### 2014-06-03 ACL2014/experiments.tex
updating experiment section

@@
+\def\qvec{\textbf{q}}
 \section{Experiments}
@@
 \centering
-\begin{tabular}{|c|r|r|}
+\begin{tabular}{|c|c|c|}
 \hline
@@
 The first data set is the one made avialble to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
-In addition, we perform evaluations using a large query log 
-from a commercial search engine, denoted as Qlogs. 
+In addition, a large query log 
+from a commercial search engine, denoted as Qlogs, is used for evaluations.
 As Qlogs typically reaches to hundres of millions of queries over multiple days (i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive set of queries posed to the search engine.}.) We then generated multiple datasets from Qlogs by sampling at various size rates.
 \dataA represents a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs.
-For each query, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion).   
-Specifically, each dimension in the feature vector of a query $q$ corresponds to a webpage (urls) that have received a user click for $q$. The weight of 
-an url feature for a query $q$ depends on the click through rate of this url for the query $q$.  
-As a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
+For each query $q$, a feature vector in a high dimensional feature space is defined as
+$\qvec = (f_1, f_2, \cdots, f_D)$, where $f_i$ is a click through rate of url $i$ and query $q$.
+%For each query $q$, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion).
+Specifically, each dimension in the feature vector of $q$ corresponds to a weight of a webpage (urls) that have received a user click for $q$.
+The weight of an url for $q$ is defined as the click through rate of the url.
+Note that in a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
 Table \ref{tab:data} summarizes the statistics of our query-log datasets.
 
-\paragraph{Test Data}: We conduct all the experiments using $2000$ random queries sampled from the query logs as the test set of queries. 
-For evaluation, we compute the true similar candidates for all the $2000$ test queries by calculating cosine similarity 
-between each test query and all the queries in the rest of the dataset. For most of the experiments, we set the similarity threshold  $\tau=0.7$, 
-meaning that the algorithm needs to retrieve candidates that have cosine similarity larger than or equal to $0.7$.
+\paragraph{Test Data} All the experiments are performed using queries $Q$ randomly sampled from the query logs as the test set of $2000$ queries. 
+That is, we want to find set $T$, where $T~=~\{~l~\mid~s(q, q')~\geq~\tau~\}$, $s(q, q')$ is a cosine similiarty, and $q' \in \{\dataA, \dataB, \dataC\}$. 
+%For evaluation, we compute the true similar cafor all the $2000$ test queries by calculating cosine similarity 
+%between each test query and all the queries in the rest of the dataset. 
+For most of the experiments, we set the similarity threshold  $\tau=0.7$.
+%meaning that for $q$, candidates $q'$ having  cosine similarity of larger than or equal to $0.7$ are retrieved.
 
-\subsection{Evaluation Metrics}
+\paragraph{Evaluation Metrics}
 We use two metrics for evaluation: recall and number of comparisons. 

### 2014-06-03 ACL2014/intro.tex

@@
 %where each dimension corresponds to a clicked url.
-Given the importance of this question, it is important to design
+Given the importance of this question, it is critical to design
 algorithms that can scale to many queries over huge logs, and allow
@@
 \emph{small} number of comparisons---that is, sublinear in the dataset size---instead of brute force linear search. 
-In addition to \emph{small} number of comparisons, we aim to 
+In addition to a \emph{small} number of comparisons, we aim to 
 retrieve neighboring candidates with  $100\%$ precision and high recall.
-It is important that false positive rate (ratio of  ``incorrectly'' identifying queries as neighbors) is penalized more severely than false negative (ratio of missing ``true'' neighbors).
+It is important that false positive rate (ratio of  ``incorrectly'' identifying queries as neighbors) 
+is penalized more severely than false negative (ratio of missing ``true'' neighbors).
 
-In the case of seeking exact matches for queries, effective solutions
+When seeking exact matches for queries, effective solutions
 are based on storing values in a hash table and mapping in via hash

### 2014-06-03 ACL2014/experiments.tex
updating experiment section

@@
 We use two metrics for evaluation: recall and number of comparisons. 
-Recall of an LSH algorithm is the fraction of \emph{true} similar candidates (found using candidates returned by computing exact cosine similarity) 
+Recall of an LSH algorithm is to measure how much the algorithm is able to retrieve \emph{true} similar candidates
+%, which tells how (found using candidates returned by computing exact cosine similarity) 
 that is retrieved by the LSH algorithm.  
 The number of comparisons performed by an algorithm is computed as the average number of pairwise comparisons that is done per test query. 
-The goal of this paper is to maximize recall and minimize the number of comparisons.
+The goal of this paper is to maximize recall and to minimize the number of comparisons.
 

### 2014-06-03 ACL2014/experiments.tex
Updated experiments.tex

@@
 \paragraph{Test Data} All the experiments are performed using queries $Q$ randomly sampled from the query logs as the test set of $2000$ queries. 
-That is, we want to find set $T$, where $T~=~\{~l~\mid~s(q, q')~\geq~\tau~\}$, $s(q, q')$ is a cosine similiarty, and $q' \in \{\dataA, \dataB, \dataC\}$. 
+That is, we want to find set $T$, where $T~=~\{~l~\mid~s(q, q')~\geq~\tau~\}$, $s(q, q')$ is a cosine similiarty, and $q' \in \{\textrm{\dataA}, \textrm{\dataB}, \textrm{\dataC}\}$. 
 %For evaluation, we compute the true similar cafor all the $2000$ test queries by calculating cosine similarity 

### 2014-06-03 ACL2014/experiments.tex
updating experiment section

@@
 while fixing $K=16$ and $L=10$ for the \aol and \dataA datasets. 
-Table~\ref{tab:varyTau} shows that as expected, finding near-duplicates, when $\tau=0.9$, 
-is easier than finding nearest neighbors when $\tau=0.7$. For, rest of this paper, 
+From Table~\ref{tab:varyTau}, $\tau=0.9$ achieves higher recall than that of $\tau=0.7$.
+This is expected as finding near duplicates is easier than finding near neighbors. For, rest of this paper, 
 we fix $\tau=0.7$ as we are interested in both near-duplicates and nearest-neighbors for our test queries.

### 2014-06-03 ACL2014/experiments.tex
updating experiment section

@@
 $\qvec = (f_1, f_2, \cdots, f_D)$, where $f_i$ is a click through rate of url $i$ and query $q$.
+Note that in our real implementation, $\qvec$ follows a spare representaion omitting dimensions with zero click through rate.
 %For each query $q$, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion).
@@
 while fixing $K=16$ and $L=10$ for the \aol and \dataA datasets. 
-From Table~\ref{tab:varyTau}, $\tau=0.9$ achieves higher recall than that of $\tau=0.7$.
+Table~\ref{tab:varyTau} shows that $\tau=0.9$ achieves higher recall than that of $\tau=0.7$.
 This is expected as finding near duplicates is easier than finding near neighbors. For, rest of this paper, 

### 2014-06-03 ACL2014/intro.tex
small edits to expts

@@
 intelligent analysis to realize users' implicit intents.
-The key resource that they have to help tease out what is meant is
-their large history of requests, in the form of large scale query logs.  
+The key resource that they have to help tease out the intent is
+their large history of requests, in the form of large scale query logs, as well
+as the log of user actions on the corresponding result pages. 
 A key primitive in 
@@
 finding near-duplicate queries \cite{leeCIKM11}, spelling correction \cite{ahmadEMNLP05,liSIGIR12},  
-and diversifying search results \cite{Song11SIGIR}; and many Natural Language Processing (NLP) tasks   
+and diversifying search results \cite{Song11SIGIR}; and many other Natural Language Processing (NLP) tasks   
 such as paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 
-distributional similarity \cite{ravichandran05,agirre09,turneyVector10}, and creating sentiment lexicons from large-scale Web data \cite{velikovich10}.
+calculating distributional similarity \cite{ravichandran05,agirre09,turneyVector10}, and creating sentiment lexicons from large-scale Web data \cite{velikovich10}.
 
@@
 query of interest, and we should aim to avoid doing many ``useless''
-comparisons that confirm that queries are indeed far from it. 
+comparisons that only confirm that other queries are indeed far from it. 
 % from our experiments  using 2000 random queries to attempt to retrieve neighbors from the query logs consisting of hundreds of millions of queries.

### 2014-06-03 ACL2014/discussion.tex
Updated tex files

@@
 in order to find the ``duplicated query terms'' efficiently. 
-As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity 
+As ``near-duplicates''  among query terms typically requires ``higher'' degree of similarity 
 (relatively easier problem) than ``relatedness'', 
@@
 We also present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial 
-large-scale query logs (consisting of hundreds of millions of queries) in sublinear time.
+large-scale query logs in sublinear time. On our entire corpus (\dataC) with hundreds of millions of queries, 
+\dflipb only requires 3,427 comparisons compared to hundreds of millions of comparisons by exact brute force algorithm.
+In future, we will extend our \lsh framework to several large-scale NLP and social media applications.

### 2014-06-03 ACL2014/experiments.tex
updating experiment section
Updated tex files

@@
  \end{tabular}
-\caption{\footnotesize{Query-logs statistics}}
+\caption{\small{Query-logs statistics}}
 \label{tab:data}
@@
 \subsection{Data}
-The first data set is the one made avialble to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
+The first data set is the one made available to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
 In addition, a large query log 
 from a commercial search engine, denoted as Qlogs, is used for evaluations.
-As Qlogs typically reaches to hundres of millions of queries over multiple days (i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive set of queries posed to the search engine.}.) We then generated multiple datasets from Qlogs by sampling at various size rates.
-\dataA represents a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs.
+As Qlogs typically reaches to hundreds of millions of queries over multiple days 
+(i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive 
+set of queries posed to the search engine.}.) We then generated multiple 
+datasets from Qlogs by sampling at various size rates. \dataA represents 
+a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs. 
 For each query $q$, a feature vector in a high dimensional feature space is defined as
 $\qvec = (f_1, f_2, \cdots, f_D)$, where $f_i$ is a click through rate of url $i$ and query $q$. 
-Note that in our real implementation, $\qvec$ follows a spare representaion omitting dimensions with zero click through rate.
+Note that in our real implementation, $\qvec$ is represented as a spare feature vector with only non-zero click through rate features. 
 %For each query $q$, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion).
@@
 The weight of an url for $q$ is defined as the click through rate of the url.
-Note that in a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
+In a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
 Table \ref{tab:data} summarizes the statistics of our query-log datasets.
@@
 \paragraph{Test Data} All the experiments are performed using queries $Q$ randomly sampled from the query logs as the test set of $2000$ queries. 
-That is, we want to find set $T$, where $T~=~\{~l~\mid~s(q, q')~\geq~\tau~\}$, $s(q, q')$ is a cosine similiarty, and $q' \in \{\textrm{\dataA}, \textrm{\dataB}, \textrm{\dataC}\}$. 
+That is, we want to find set $T$, where $T~=~\{~l~\mid~s(q, q')~\geq~\tau~\}$, $s(q, q')$ is a cosine similarity, and $q' \in \{\textrm{\dataA}, \textrm{\dataB}, \textrm{\dataC}\}$. 
 %For evaluation, we compute the true similar cafor all the $2000$ test queries by calculating cosine similarity 
@@
 We use two metrics for evaluation: recall and number of comparisons. 
-Recall of an LSH algorithm is to measure how much the algorithm is able to retrieve \emph{true} similar candidates
+Recall of an \lsh algorithm is to measure how much the algorithm is able to retrieve \emph{true} similar candidates
 %, which tells how (found using candidates returned by computing exact cosine similarity) 
-that is retrieved by the LSH algorithm.  
+that is retrieved by the \lsh algorithm.  
 The number of comparisons performed by an algorithm is computed as the average number of pairwise comparisons that is done per test query. 
@@
 
-\subsection{Evaluating Vanilla LSH} 
+\subsection{Evaluating Vanilla \lsh} 
 \label{subsec:eval:vanillaLSH}
@@
  \end{tabular}
-\caption{\footnotesize{Varying $\tau$ with fixed $K=16$ and $L=10$ on \aol and \dataA.}}
+\caption{\small{Varying $\tau$ with fixed $K=16$ and $L=10$ on \aol and \dataA.}}
 \label{tab:varyTau}
@@
 Table~\ref{tab:varyTau} shows that $\tau=0.9$ achieves higher recall than that of $\tau=0.7$.
-This is expected as finding near duplicates is easier than finding near neighbors. For, rest of this paper, 
-we fix $\tau=0.7$ as we are interested in both near-duplicates and nearest-neighbors for our test queries.
+This is expected as finding near duplicates is easier than finding near neighbors. For the rest of this paper, 
+ $\tau$ is set as $0.7$ since we are interested in both near-duplicates and nearest-neighbors for our test queries.
 
@@
 Recall that $L$ denotes the number of hash tables and $K$ is the width of the index of the buckets in the table. 
-Increasing $K$ results in increase of the precision by reducing the false positive candidates, but 
-the $L$ also need to be correspondingly increased in order the maintain a good recall
+Increasing the $K$ results in increase of the precision by reducing the false positive candidates, but 
+$L$ also need to be correspondingly increased in order to maintain a good recall
 (i.e. reduce false negatives). 
 Table \ref{tab:varyL} shows that increasing $L$ leads to better recall, 
-but at the expense of performing more comparisons on both the datasets. 
+but at the expense of conducting more comparisons on both the datasets. 
 In addition, having a large $L$ 
@@
  \end{tabular}
-\caption{\footnotesize{Varying $L$ with fixed $K=16$ on \aol and \dataA with $\tau=0.7$.}}
+\caption{\small{Varying $L$ with fixed $K=16$ on \aol and \dataA with $\tau=0.7$.}}
 \label{tab:varyL}
@@
  \end{tabular}
-\caption{\footnotesize{Varying $K$ with fixed $L=10$ on \aol with $\tau=0.7$.}}
+\caption{\small{Varying $K$ with fixed $L=10$ on \aol with $\tau=0.7$.}}
 \label{tab:varyK}
@@
 
-\begin{table}
+\begin{table}[h]
 \centering
@@
  \end{tabular}
-\caption{\footnotesize{Fixed $K=16$  and $L=10$ on different sized datasets with $\tau=0.7$.}}
+\caption{\small{Fixed $K=16$  and $L=10$ on different sized datasets with $\tau=0.7$.}}
 \label{tab:varyData}
@@
  \end{tabular}
-\caption{\footnotesize{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ on different sized datasets.}}
+\caption{\small{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ on different sized datasets.}}
 \label{tab:bestLSH}
@@
  }
-\caption{\footnotesize{Flipping the bits in the query only with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
+\caption{\small{Flipping the bits in the query only with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
 \label{tab:query:aol}
@@
  }
-\caption{\footnotesize{Flipping the bits in both the query and the database with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
+\caption{\small{Flipping the bits in both the query and the database with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
 \label{tab:both:aol}
@@
  }
-\caption{\footnotesize{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ and $F=2$ on different sized datasets with $\tau=0.7$.}}
+\caption{\small{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ and $F=2$ on different sized datasets with $\tau=0.7$.}}
 \label{tab:dataset:final}
@@
 
-\subsection{Evaluating Multi-Probe LSH}
+\subsection{Evaluating Multi-Probe \lsh}
 \label{subsec:eval:multiProbeLSH}

### 2014-06-03 ACL2014/relatedwork.tex
Updated tex files

@@
 existing work deals with approximating cosine similarity by Hamming distance  
-\cite{ravichandran05,vandurme-lall:2010:Short,vandurme-lall:2011:Short,goyal12Flag}. 
-In that problem setting, the goal is to minimize both false positives and negatives. 
-In our work, we focus on minimizing false negatives with zero tolerance for false positives.
+\cite{ravichandran05,vandurme-lall:2010:Short,vandurme-lall:2011:Short,goyal12Flag,moranACL13}.
+Moran et al.
+\shortcite{moranACL13} recently proposed a data-driven non-uniform bit allocation across hyperplanes that uses less bits than many existing \lsh schemes to approximate cosine similarity by Hamming distance.
+In all these existing problem settings, the goal is to minimize both false positives and negatives. However, we focus on minimizing false negatives with zero tolerance for false positives.
 

### 2014-06-03 ACL2014/system.tex
Updated tex files

@@
 \begin{figure}[ht]
-%\small
+\small
 \fbox{
@@
 In this work, we have implemented the above algorithm in a map-reduce setting (Hadoop). 
+\lsh algorithm is incredibly easy to implement in map-reduce setting; hence due to limited space, 
+we do not include the unnecessary implementation details of this algorithm.  
 In Section \ref{subsec:eval:vanillaLSH}, we show that the map-reduce implementation scales to hundreds of millions of queries.
@@
 
+In this work, we have implemented all the above four variants of \lsh in a map-reduce setting (Hadoop). 
+It is incredibly easy to change the existing vanilla \lsh map-reduce implementation to implement 
+these four novel variants of \lsh.  
+In Section \ref{subsec:eval:multiProbeLSH}, we show that the map-reduce implementation of four novel variants of \lsh scales to hundreds of millions of queries.
+
 %we have experimented with is the following variant of Multi-probe \lsh:  first we compute the initial \lsh of a query q, which gives the $L$ bucket ids.
